### 2018-08-08 paper/paper.tex
adding female age distribution histogram

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}

% spanish symbols for narrative
\usepackage[utf8]{inputenc} 
% language
\usepackage[spanish]{babel}

%changing from roman number to integers
\renewcommand{\thesection}{\arabic{section}}
\renewcommand{\thesubsection}{\arabic{section}.\arabic{subsection}}

\usepackage{pgfplots}
\usepackage{pgfplotstable}
    \pgfplotsset{
        % use this `compat' level or higher to position the bars in one group
        % next to each other
        compat=1.7,
    }
    % load the data table ...
    \pgfplotstableread[col sep=comma]{femaleAgeDistribution.csv}{\femaleAgeDistribution}
        % and store the number of columns in `\NoOfCols'
        % (minus 1 because counting in `\foreach' starts with zero
        \pgfplotstablegetcolsof{\femaleAgeDistribution}
        \pgfmathtruncatemacro{\NoOfCols}{\pgfplotsretval-1}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Título\\
}

\author{\IEEEauthorblockN{Autores}
\IEEEauthorblockA{
\textit{Grupo de Investigación de Aprendizaje Profundo} \\
\textit{Departamento Ingeniería en Sistemas de Información}\\
\textit{Universidad Tecnológica Nacional}\\
\textit{Facultad Regional Rosario}\\
mail@frro.utn.edu.ar} %should be hyperlink
}

\maketitle

\renewcommand{\abstractname}{Abstract} %Ajustes por traducción a español
\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

\renewcommand{\IEEEkeywordsname}{Palabras Clave} %Ajustes por traducción a español
\begin{IEEEkeywords}
aprendizaje profundo, red neuronal convolucional, rsna, procesamiento de imagenes
\end{IEEEkeywords}

\section{Introducción}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

\section{Metodología y Objetivos}

\subsection{Conjunto de datos}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

% used PGFPlots v1.14

\begin{tikzpicture}
    \begin{semilogyaxis}[
        % adjust the `width' a bit by keeping the default `height'
        width=1.05*\axisdefaultwidth,
        height=\axisdefaultheight,
        % set appropriate `ymax' value so the `nodes near coords' fit to the plot
        % (adjusting the `ymin' value is just to make it look a little bit better)
        ymin=0,
        ymax=2000,
        % there should be no gap between the bars in one group
        ybar=0pt,
        % use data from the table for the xticklabels
        xtick=data,
        xticklabels from table={\femaleAgeDistribution}{Anio},
        % adjust the size of the bars so they don't overlap
        % (you can play with the numerator to change the gap between the groups)
        bar width=0.6/\NoOfCols,
        % enlarge the x limits so all of the bars are shown
        % (play with the value to adjust the gap on the sides of the plot)
        enlarge x limits={abs=0.6},
        % and position the legend outside of the plot to not overlap with the data
        %legend pos=outer north east,
        % add `nodes near coords'
        nodes near coords={
            % because internally PGFPlots works with floating point numbers, we
            % change them to fixed point numbers
            \pgfkeys{
                /pgf/fpu=true,
                /pgf/fpu/output format=fixed,
            }
            % truncate value count to integer
            \pgfmathparse{\pgfplotspointmeta}
            \pgfmathprintnumber{\pgfmathresult}\,
        },
        % set the style of the `nodes near coords'
        nodes near coords style={
            font=\tiny,
            rotate=90,
            anchor=west,
        },
        % as basis for the `nodes near coords' use the raw y values
        point meta=rawy,
    ]
        % add the data rows for each column 
        \foreach \i in {1,...,\NoOfCols} {
            \addplot table [
                x expr=\coordindex,
                y index=\i,
                col sep=comma,
            ] {\femaleAgeDistribution};
                % to automatically add the legend entries first extract the
                % column name and store it in `\colname'
                    \pgfplotstablegetcolumnnamebyindex{\i}\of{\femaleAgeDistribution}\to{\colname}
                % now you can add the legend entry
                % (because we are in a loop we have to use the "expanded" version)
                \addlegendentryexpanded{\colname};
        }
    \end{semilogyaxis}
\end{tikzpicture}

\subsection{Preprocesamiento}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Modelos}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\section{Resultados del experimento}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\section{Conclusiones y Trabajo Futuro}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Conclusiones}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Trabajo Futuro}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}

\end{document}

### 2018-08-09 main.py
code cleaning

@@ -104,19 +104,19 @@ if CNN == "IV3":
     # base_iv3_model = InceptionV3(include_top=False, weights="imagenet")
     base_iv3_model = InceptionV3(weights="imagenet")
     # Inception V3 output from input layer
-    output_vgg16 = base_iv3_model(image_input)
+    output_cnn = base_iv3_model(image_input)
     # flattening it #why?
     # flat_iv3 = Flatten()(output_vgg16)
 elif CNN == "RN50":
     # ResNet50 layer with pre-trained weights from ImageNet
     base_rn50_model = ResNet50(weights="imagenet")
     # ResNet50 output from input layer
-    output_rn50 = base_rn50_model(image_input)
+    output_cnn = base_rn50_model(image_input)
 elif CNN == "Xception":
     # Xception layer with pre-trained weights from ImageNet
     base_xp_model = Xception(weights="imagenet")
     # Xception output from input layer
-    output_xp = base_xp_model(image_input)
+    output_cnn = base_xp_model(image_input)
 
 # Gender input layer
 gdr_input = Input(shape=(1,), name="gdr_input")
@@ -125,15 +125,8 @@ gdr_dense = Dense(32, activation="relu")
 # Gender dense output
 output_gdr_dense = gdr_dense(gdr_input)
 
-if CNN == "IV3":
-    # Concatenating iv3 output with sex_dense output after going through shared layer
-    x = keras.layers.concatenate([output_vgg16, output_gdr_dense])
-elif CNN == "RN50":
-    # Concatenating ResNet50 output with gender_dense output after going through shared layer
-    x = keras.layers.concatenate([output_rn50, output_gdr_dense])
-elif CNN == "Xception":
-    # Concatenating Xception output with gender_dense output after going through shared layer
-    x = keras.layers.concatenate([output_xp, output_gdr_dense])
+# Concatenating CNN output with sex_dense output after going through shared layer
+x = keras.layers.concatenate([output_cnn, output_gdr_dense])
 
 # We stack dense layers and dropout layers to avoid overfitting after that
 x = Dense(1000, activation="relu")(x)
@@ -156,7 +149,7 @@ print(model.summary())
 
 # Load weight
 if args["load_weights"] != None:
-    print("Loading weights for", args["load_weights"])
+    print("Loading weights from", args["load_weights"])
     model.load_weights(args["load_weights"])
 
 model.compile(optimizer=OPTIMIZER, loss="mean_squared_error", metrics=["MAE", "accuracy"])

### 2018-08-09 paper/paper.tex

@@
 
-% spanish symbols for narrative
-\usepackage[utf8]{inputenc} 
-% language
-\usepackage[spanish]{babel}
+\usepackage[utf8]{inputenc} % Acentos, etc
+\usepackage[spanish]{babel} % Idioma
 
-%changing from roman number to integers
-\renewcommand{\thesection}{\arabic{section}}
-\renewcommand{\thesubsection}{\arabic{section}.\arabic{subsection}}
-
-\usepackage{pgfplots}
-\usepackage{pgfplotstable}
-    \pgfplotsset{
-        % use this `compat' level or higher to position the bars in one group
-        % next to each other
-        compat=1.7,
-    }
-    % load the data table ...
-    \pgfplotstableread[col sep=comma]{femaleAgeDistribution.csv}{\femaleAgeDistribution}
-        % and store the number of columns in `\NoOfCols'
-        % (minus 1 because counting in `\foreach' starts with zero
-        \pgfplotstablegetcolsof{\femaleAgeDistribution}
-        \pgfmathtruncatemacro{\NoOfCols}{\pgfplotsretval-1}
+\renewcommand{\thesection}{\arabic{section}} %Se cambia de números romanos a número
+\renewcommand{\thesubsection}{\arabic{section}.\arabic{subsection}} %Se cambia de %números romanos a número
 
@@
 \title{Título\\
+%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
+%should not be used}
+%\thanks{Identify applicable funding agency here. If none, delete this.}
 }
@@
 \textit{Facultad Regional Rosario}\\
-mail@frro.utn.edu.ar} %should be hyperlink
+mail@frro.utn.edu.ar} %hacerlo hyperlink
 }
@@
 Please do not revise any of the current designations.
-
-% used PGFPlots v1.14
-
-\begin{tikzpicture}
-    \begin{semilogyaxis}[
-        % adjust the `width' a bit by keeping the default `height'
-        width=1.05*\axisdefaultwidth,
-        height=\axisdefaultheight,
-        % set appropriate `ymax' value so the `nodes near coords' fit to the plot
-        % (adjusting the `ymin' value is just to make it look a little bit better)
-        ymin=0,
-        ymax=2000,
-        % there should be no gap between the bars in one group
-        ybar=0pt,
-        % use data from the table for the xticklabels
-        xtick=data,
-        xticklabels from table={\femaleAgeDistribution}{Anio},
-        % adjust the size of the bars so they don't overlap
-        % (you can play with the numerator to change the gap between the groups)
-        bar width=0.6/\NoOfCols,
-        % enlarge the x limits so all of the bars are shown
-        % (play with the value to adjust the gap on the sides of the plot)
-        enlarge x limits={abs=0.6},
-        % and position the legend outside of the plot to not overlap with the data
-        %legend pos=outer north east,
-        % add `nodes near coords'
-        nodes near coords={
-            % because internally PGFPlots works with floating point numbers, we
-            % change them to fixed point numbers
-            \pgfkeys{
-                /pgf/fpu=true,
-                /pgf/fpu/output format=fixed,
-            }
-            % truncate value count to integer
-            \pgfmathparse{\pgfplotspointmeta}
-            \pgfmathprintnumber{\pgfmathresult}\,
-        },
-        % set the style of the `nodes near coords'
-        nodes near coords style={
-            font=\tiny,
-            rotate=90,
-            anchor=west,
-        },
-        % as basis for the `nodes near coords' use the raw y values
-        point meta=rawy,
-    ]
-        % add the data rows for each column 
-        \foreach \i in {1,...,\NoOfCols} {
-            \addplot table [
-                x expr=\coordindex,
-                y index=\i,
-                col sep=comma,
-            ] {\femaleAgeDistribution};
-                % to automatically add the legend entries first extract the
-                % column name and store it in `\colname'
-                    \pgfplotstablegetcolumnnamebyindex{\i}\of{\femaleAgeDistribution}\to{\colname}
-                % now you can add the legend entry
-                % (because we are in a loop we have to use the "expanded" version)
-                \addlegendentryexpanded{\colname};
-        }
-    \end{semilogyaxis}
-\end{tikzpicture}
 

### 2018-08-10 deep_cut_hands.py
Get image histograma

@@ -1,72 +1,197 @@
 #!/usr/bin/python3
-# python keras_mnist.py --output output/keras_mnist.png
 
-# import the necessary packages
-from sklearn.preprocessing import LabelBinarizer
-from sklearn.model_selection import train_test_split
-from sklearn.metrics import classification_report
-from keras.models import Sequential
-from keras.layers.core import Dense
-from keras.optimizers import SGD
-from sklearn import datasets
-import matplotlib.pyplot as plt
+import cv2
+import fnmatch
 import numpy as np
-import argparse
+import os
+import pandas as pd
+import sys
 
-# construct the argument parse and parse the arguments
-ap = argparse.ArgumentParser()
-ap.add_argument(
-    "-o", "--output", required=True, help="path to the output loss/accuracy plot"
-)
-args = vars(ap.parse_args())
+# Directory of dataset to use
+TRAIN_DIR = "dataset_sample"
+# TRAIN_DIR = "boneage-training-dataset"
 
-# grab the MNIST dataset (if this is your first time running this
-# script, the download may take a minute -- the 55MB MNIST dataset
-# will be downloaded)
-print("[INFO] loading MNIST (full) dataset...")
-dataset = datasets.fetch_mldata("MNIST Original")
-# scale the raw pixel intensities to the range [0, 1.0], then
-# construct the training and testing splits
-data = dataset.data.astype("float") / 255.0
-(trainX, testX, trainY, testY) = train_test_split(data, dataset.target, test_size=0.25)
+# Use N images of dataset, If it is -1 using all dataset
+CUT_DATASET = 1000
+# Sort dataset randomly
+SORT_RANDOMLY = not True
 
-# convert the labels from integers to vectors
-lb = LabelBinarizer()
-trainY = lb.fit_transform(trainY)
-testY = lb.transform(testY)
+# Turn saving renders feature on/off
+SAVE_RENDERS = False
 
-# define the 784-256-128-10 architecture using Keras
-model = Sequential()
-model.add(Dense(256, input_shape=(784,), activation="sigmoid"))
-model.add(Dense(128, activation="sigmoid"))
-model.add(Dense(10, activation="softmax"))
+# Create intermediate images in separate folders for debugger.
+# mask, cut_hand, delete_object, render
+SAVE_IMAGE_FOR_DEBUGGER = False
 
-# train the model using SGD
-print("[INFO] training network...")
-sgd = SGD(0.01)
[…]

### 2018-08-10 deep_cut_hands.py
Create model to predict values

@@ -1,7 +1,15 @@
 #!/usr/bin/python3
 
+from keras.applications import InceptionV3, ResNet50, Xception
+from keras.layers import Flatten, Dense, Input, Dropout
+from keras.models import Model, Sequential
+from keras.optimizers import Adam, RMSprop, Adadelta, Adagrad
+from six.moves import cPickle
+import argparse
 import cv2
 import fnmatch
+import keras
+import matplotlib.pyplot as plt
 import numpy as np
 import os
 import pandas as pd
@@ -13,19 +21,24 @@ TRAIN_DIR = "dataset_sample"
 
 # Use N images of dataset, If it is -1 using all dataset
 CUT_DATASET = 1000
+
+# network and training
+EPOCHS = 500
+BATCH_SIZE = 10
+
+# https://keras.io/optimizers
+# OPTIMIZER = Adam(lr=0.001)
+# OPTIMIZER = RMSprop()
+OPTIMIZER = Adadelta(lr=1.0, rho=0.95, epsilon=None, decay=0.0)
+# OPTIMIZER = Adagrad(lr=0.05)
+
 # Sort dataset randomly
-SORT_RANDOMLY = not True
+SORT_RANDOMLY = True
 
-# Turn saving renders feature on/off
-SAVE_RENDERS = False
-
-# Create intermediate images in separate folders for debugger.
-# mask, cut_hand, delete_object, render
-SAVE_IMAGE_FOR_DEBUGGER = False
-
-# Extracting hands from images and using that new dataset.
-# Simple dataset is correct, I am verifying the original.
-EXTRACTING_HANDS = True
+# construct the argument parse and parse the arguments
+ap = argparse.ArgumentParser()
+ap.add_argument("-lw", "--load_weights", help="Path to the file weights")
+args = vars(ap.parse_args())
 
 # For this problem the validation and test data provided by the concerned authority did not have labels,
 # so the training data was split into train, test and validation sets
@@ -34,6 +47,13 @@ __location__ = os.path.realpath(os.path.join(os.getcwd(), os.path.dirname(__file
 train_dir = os.path.join(__location__, TRAIN_DIR)
 
 img_file = ""
+
+# Turn saving renders feature on/off
+SAVE_RENDERS = False
+
+# Create intermediate images in separate folders for debugger.
+# mask, cut_hand, delete_object, render
+SAVE_IMAGE_FOR_DEBUGGER = False
 
 
 # Show the images
[…]

### 2018-08-11 deep_cut_hands.py
Add arg and show socre

@@ -38,6 +38,9 @@ SORT_RANDOMLY = True
 # construct the argument parse and parse the arguments
 ap = argparse.ArgumentParser()
 ap.add_argument("-lw", "--load_weights", help="Path to the file weights")
+ap.add_argument("-tb", "--tensorBoard", help="Active tensorBoard")
+ap.add_argument("-rl", "--reduce_learning", help="Active reduce learning rate")
+ap.add_argument("-not_cp", "--not_checkpoint", help="Active checkpoint")
 args = vars(ap.parse_args())
 
 # For this problem the validation and test data provided by the concerned authority did not have labels,
@@ -240,7 +243,16 @@ def loadCallBack():
     )
     print("tensorboard --logdir", LOG_DIR_TENSORBOARD)
 
-    return [tbCallBack, checkpoint, reduceLROnPlat]
+    cb = []
+
+    if args["tensorBoard"] != None:
+        cb.append(tbCallBack)
+    if args["not_checkpoint"] == None:
+        cb.append(checkpoint)
+    if args["reduce_learning"] != None:
+        cb.append(reduceLROnPlat)
+
+    return cb
 
 
 # Como vamos a usar multi procesos uno por core.
@@ -350,8 +362,10 @@ if __name__ == "__main__":
 
     print("Test score:", score)
     print("Test loss:", score[0])
-    print("Test MAE:", score[1])
-    print("Test MSE:", score[2])
+
+    print("Test loss:", score[1], score[2])
+    print("Test MAE:", score[3], score[4])
+    print("Test MSE:", score[5], score[6])
 
     # list all data in history
     print("\n[INFO] Save model history graphics...")

### 2018-08-11 deep_cut_hands.py
Fix show score and load weight

@@ -209,11 +209,6 @@ def checkPath():
             print("\n[INFO] Create folder render")
             os.makedirs(os.path.join(__location__, TRAIN_DIR, "render"))
 
-    # Load weight
-    if args["load_weights"] != None:
-        print("Loading weights from", args["load_weights"])
-        model.load_weights(args["load_weights"])
-
 
 def loadCallBack():
     checkpoint = keras.callbacks.ModelCheckpoint(
@@ -325,6 +320,11 @@ if __name__ == "__main__":
     print("\n[INFO] Model summary")
     print(model.summary())
 
+    # Load weight
+    if args["load_weights"] != None:
+        print("Loading weights from", args["load_weights"])
+        model.load_weights(args["load_weights"])
+
     print("\n[INFO] Training network...")
     model.compile(loss="mean_squared_error", metrics=["MAE", "MSE"], optimizer=OPTIMIZER)
 
@@ -360,7 +360,6 @@ if __name__ == "__main__":
         [hist_test], [lower_test, upper_test], batch_size=BATCH_SIZE, verbose=1
     )
 
-    print("Test score:", score)
     print("Test loss:", score[0])
 
     print("Test loss:", score[1], score[2])

### 2018-08-11 deep_cut_hands.py
New model

@@ -297,19 +297,17 @@ if __name__ == "__main__":
 
     x_lower = Dense(256, activation="sigmoid")(hist_input)
     x_lower = Dense(256, activation="relu")(x_lower)
-    x_lower = Dense(200, activation="relu")(x_lower)
+    #x_lower = Dense(200, activation="relu")(x_lower)
     x_lower = Dense(128, activation="relu")(x_lower)
-    x_lower = Dense(64, activation="sigmoid")(x_lower)
-    x_lower = Dense(16, activation="relu")(x_lower)
-    x_lower = Dense(2, activation="relu")(x_lower)
+    #x_lower = Dense(32, activation="relu")(x_lower)
+    #x_lower = Dense(16, activation="relu")(x_lower)
 
     x_upper = Dense(256, activation="sigmoid")(hist_input)
     x_upper = Dense(256, activation="relu")(x_upper)
-    x_upper = Dense(200, activation="relu")(x_upper)
+    #x_upper = Dense(200, activation="relu")(x_upper)
     x_upper = Dense(128, activation="relu")(x_upper)
-    x_upper = Dense(64, activation="sigmoid")(x_upper)
-    x_upper = Dense(16, activation="relu")(x_upper)
-    x_upper = Dense(2, activation="relu")(x_upper)
+    #x_upper = Dense(32, activation="relu")(x_upper)
+    #x_upper = Dense(2, activation="relu")(x_upper)
 
     # Prediction for the upper and lower value
     lower_output = Dense(1, name="lower")(x_lower)
@@ -360,11 +358,9 @@ if __name__ == "__main__":
         [hist_test], [lower_test, upper_test], batch_size=BATCH_SIZE, verbose=1
     )
 
-    print("Test loss:", score[0])
-
-    print("Test loss:", score[1], score[2])
-    print("Test MAE:", score[3], score[4])
-    print("Test MSE:", score[5], score[6])
+    print("Test loss:", score[0], score[3])
+    print("Test MAE:", score[1], score[4])
+    print("Test MSE:", score[2], score[5])
 
     # list all data in history
     print("\n[INFO] Save model history graphics...")

### 2018-08-11 deep_cut_hands.py
Sort score

@@ -358,9 +358,9 @@ if __name__ == "__main__":
         [hist_test], [lower_test, upper_test], batch_size=BATCH_SIZE, verbose=1
     )
 
-    print("Test loss:", score[0], score[3])
-    print("Test MAE:", score[1], score[4])
-    print("Test MSE:", score[2], score[5])
+    print("Test loss:", score[1], score[4])
+    print("Test MAE:", score[3], score[5])
+    print("Test MSE:", score[0], score[2])
 
     # list all data in history
     print("\n[INFO] Save model history graphics...")

### 2018-08-11 deep_cut_hands.py
Modular code

@@ -1,4 +1,5 @@
 #!/usr/bin/python3
+# ./deep_cut_hands.py -lw ./model-backup/cut-hand/model.h5
 
 from keras.applications import InceptionV3, ResNet50, Xception
 from keras.layers import Flatten, Dense, Input, Dropout
@@ -9,7 +10,6 @@ import argparse
 import cv2
 import fnmatch
 import keras
-import matplotlib.pyplot as plt
 import numpy as np
 import os
 import pandas as pd
@@ -24,12 +24,12 @@ CUT_DATASET = 1000
 
 # network and training
 EPOCHS = 500
-BATCH_SIZE = 10
+BATCH_SIZE = 15
 
 # https://keras.io/optimizers
 # OPTIMIZER = Adam(lr=0.001)
-# OPTIMIZER = RMSprop()
-OPTIMIZER = Adadelta(lr=1.0, rho=0.95, epsilon=None, decay=0.0)
+OPTIMIZER = RMSprop()
+# OPTIMIZER = Adadelta(lr=1.0, rho=0.95, epsilon=None, decay=0.0)
 # OPTIMIZER = Adagrad(lr=0.05)
 
 # Sort dataset randomly
@@ -41,6 +41,7 @@ ap.add_argument("-lw", "--load_weights", help="Path to the file weights")
 ap.add_argument("-tb", "--tensorBoard", help="Active tensorBoard")
 ap.add_argument("-rl", "--reduce_learning", help="Active reduce learning rate")
 ap.add_argument("-not_cp", "--not_checkpoint", help="Active checkpoint")
+ap.add_argument("-t", "--train", help="Run train model")
 args = vars(ap.parse_args())
 
 # For this problem the validation and test data provided by the concerned authority did not have labels,
@@ -250,20 +251,47 @@ def loadCallBack():
     return cb
 
 
-# Como vamos a usar multi procesos uno por core.
-# Los procesos hijos cargan el mismo código.
-# Este if permite que solo se ejecute lo que sigue si es llamado
-# como proceso raíz.
-if __name__ == "__main__":
-    checkPath()
+def makerModel():
+    # First we need to create a model structure
+    hist_input = Input(shape=(256,), name="hist_input")
 
-    files = getFiles()
-    (X_train, y_lower, y_upper) = loadDataSet(files)
+    x_lower = Dense(256, activation="sigmoid")(hist_input)
+    x_lower = Dense(256, activation="relu")(x_lower)
[…]

### 2018-08-11 deep_cut_hands.py
Fix arg

@@ -24,12 +24,12 @@ CUT_DATASET = 1000
 
 # network and training
 EPOCHS = 500
-BATCH_SIZE = 15
+BATCH_SIZE = 1
 
 # https://keras.io/optimizers
 # OPTIMIZER = Adam(lr=0.001)
-OPTIMIZER = RMSprop()
-# OPTIMIZER = Adadelta(lr=1.0, rho=0.95, epsilon=None, decay=0.0)
+# OPTIMIZER = RMSprop()
+OPTIMIZER = Adadelta(lr=1.0, rho=0.95, epsilon=None, decay=0.0)
 # OPTIMIZER = Adagrad(lr=0.05)
 
 # Sort dataset randomly
@@ -37,11 +37,16 @@ SORT_RANDOMLY = True
 
 # construct the argument parse and parse the arguments
 ap = argparse.ArgumentParser()
-ap.add_argument("-lw", "--load_weights", help="Path to the file weights")
-ap.add_argument("-tb", "--tensorBoard", help="Active tensorBoard")
-ap.add_argument("-rl", "--reduce_learning", help="Active reduce learning rate")
-ap.add_argument("-not_cp", "--not_checkpoint", help="Active checkpoint")
-ap.add_argument("-t", "--train", help="Run train model")
+ap.add_argument("-lw", "--load_weights",
+                help="Path to the file weights")
+ap.add_argument("-tb", "--tensorBoard", default=False,
+                help="Active tensorBoard")
+ap.add_argument("-rl", "--reduce_learning", default=False,
+                help="Active reduce learning rate")
+ap.add_argument("-cp", "--checkpoint", default=True,
+                help="Active checkpoint")
+ap.add_argument("-t", "--train", default=True,
+                help="Run train model")
 args = vars(ap.parse_args())
 
 # For this problem the validation and test data provided by the concerned authority did not have labels,
@@ -241,11 +246,11 @@ def loadCallBack():
 
     cb = []
 
-    if args["tensorBoard"] != None:
+    if args["tensorBoard"] == True:
         cb.append(tbCallBack)
-    if args["not_checkpoint"] == None:
+    if args["checkpoint"] == True:
         cb.append(checkpoint)
-    if args["reduce_learning"] != None:
+    if args["reduce_learning"] == True:
         cb.append(reduceLROnPlat)
 
     return cb
@@ -373,6 +378,6 @@ if __name__ == "__main__":
     (X_train, y_lower, y_upper) = loadDataSet(files)
[…]

### 2018-08-11 deep_cut_hands.py
Add histogram for train

@@ -193,17 +193,21 @@ def getFiles():
         if CUT_DATASET <= 0 or len(rta) < CUT_DATASET:
             # Get row with id equil image's name
             csv_row = df[df.id == int(file_name[:-4])]
-            # Get lower color
-            lower = csv_row.lower.tolist()[0]
-            # Get upper color
-            upper = csv_row.upper.tolist()[0]
 
-            rta.append((file_name, lower, upper))
+            # Get lower color
+            lower = csv_row.lower.tolist()
+            # Get upper color
+            upper = csv_row.upper.tolist()
+            if not(lower[0] != lower[0] and upper[0] != upper[0]):
+                rta.append((file_name, lower[0], upper[0]))
+            else:
+                print("Not data for", file_name)
 
     return rta
 
-
 # Create the directories to save the images
+
+
 def checkPath():
     if SAVE_IMAGE_FOR_DEBUGGER:
         for folder in ["histograms_level_fix", "cut_hand", "render", "mask"]:
@@ -380,4 +384,11 @@ if __name__ == "__main__":
     model = makerModel()
     if args["train"] == True:
         trainModel(model, X_train, y_lower, y_upper)
-    # else:
+    else:
+        print("\n[INFO] Predict...")
+        # new instance where we do not know the answer
+        Xnew = X_train[19]
+        # make a prediction
+        ynew = model.predict(Xnew)
+        # show the inputs and predicted outputs
+        print("X=%s, Predicted=%s" % (Xnew[0], ynew[0]))

### 2018-08-11 deep_cut_hands.py
Fix for show predict

@@ -1,5 +1,6 @@
 #!/usr/bin/python3
 # ./deep_cut_hands.py -lw ./model-backup/cut-hand/model.h5
+# ./deep_cut_hands.py --train False -lw ./model-backup/cut-hand/model.h5
 
 from keras.applications import InceptionV3, ResNet50, Xception
 from keras.layers import Flatten, Dense, Input, Dropout
@@ -191,9 +192,9 @@ def getFiles():
     for file_name in files:
         # Cut list of file
         if CUT_DATASET <= 0 or len(rta) < CUT_DATASET:
+            # print(file_name)
             # Get row with id equil image's name
             csv_row = df[df.id == int(file_name[:-4])]
-
             # Get lower color
             lower = csv_row.lower.tolist()
             # Get upper color
@@ -387,8 +388,9 @@ if __name__ == "__main__":
     else:
         print("\n[INFO] Predict...")
         # new instance where we do not know the answer
-        Xnew = X_train[19]
+        Xnew = X_train
+        Xnew = np.array(Xnew)
         # make a prediction
         ynew = model.predict(Xnew)
         # show the inputs and predicted outputs
-        print("X=%s, Predicted=%s" % (Xnew[0], ynew[0]))
+        print("Lower: %s, Upper: %s" % (ynew[0][0], ynew[1][0]))

### 2018-08-11 deep_cut_hands.py
Fix print

@@ -292,7 +292,7 @@ def makerModel():
 
     # Load weight
     if args["load_weights"] != None:
-        print("Loading weights from", args["load_weights"])
+        print("\n[INFO] Loading weights from", args["load_weights"])
         model.load_weights(args["load_weights"])
 
     return model

### 2018-08-11 deep_cut_hands.py
Show colors on terminal

@@ -14,6 +14,7 @@ import keras
 import numpy as np
 import os
 import pandas as pd
+import platform
 import sys
 
 # Directory of dataset to use
@@ -72,68 +73,6 @@ def writeImage(path, image, force=False):
         cv2.imwrite(os.path.join(__location__, TRAIN_DIR, path, img_file), image)
 
 
-# Auto adjust levels colors
-# We order the colors of the image with their frequency and
-# obtain the accumulated one, then we obtain the colors that
-# accumulate 2.5% and 99.4% of the frequency.
-def histogramsLevelFix(img):
-    # This function is only prepared for images in scale of gripes
-    img = cv2.cvtColor(img, cv2.COLOR_BGR2GRAY)
-    # Find the acceptable limits of the intensity histogram
-    min_color, max_color = np.percentile(img, (2.5, 99.4))
-    min_color = int(min_color)
-    max_color = int(max_color)
-
-    # To improve the preform we created a color palette with the new values
-    colors_palette = []
-    # Auxiliary calculation, avoid doing calculations within the 'for'
-    dif_color = 255 / (max_color - min_color)
-    for color in range(256):
-        if color <= min_color:
-            colors_palette.append(0)
-        elif color >= max_color:
-            colors_palette.append(255)
-        else:
-            colors_palette.append(int(round((color - min_color) * dif_color)))
-
-    # We paint the image with the new color palette
-    height, width = img.shape
-    for y in range(0, height):
-        for x in range(0, width):
-            color = img[y, x]
-            img[y, x] = colors_palette[color]
-
-    writeImage("histograms_level_fix", np.hstack([img]))  # show the images ===========
-
-    return img
-
-
-# Show a progress bar
-def updateProgress(progress, tick="", total="", status="Loading..."):
-    lineLength = 80
-    barLength = 23
-    if isinstance(progress, int):
-        progress = float(progress)
-    if progress < 0:
-        progress = 0
-        status = "Waiting...\r"
-    if progress >= 1:
-        progress = 1
-        status = "Completed loading data\r\n"
-    block = int(round(barLength * progress))
-    line = str("\rImage: {0}/{1} [{2}] {3}% {4}").format(
-        tick,
-        total,
-        str(("#" * block)) + str("." * (barLength - block)),
[…]

### 2018-08-11 deep_cut_hands.py
Add new histogram

@@ -49,6 +49,8 @@ ap.add_argument("-cp", "--checkpoint", default=True,
                 help="Active checkpoint")
 ap.add_argument("-t", "--train", default=True,
                 help="Run train model")
+ap.add_argument("-p", "--predict",
+                help="File to predict values")
 args = vars(ap.parse_args())
 
 # For this problem the validation and test data provided by the concerned authority did not have labels,
@@ -118,7 +120,7 @@ def loadDataSet(files=[]):
 def getFiles():
     rta = []
     # Read csv
-    df = pd.read_csv(os.path.join(train_dir, "histograma-dataset.csv"))
+    df = pd.read_csv(os.path.join(train_dir, "histogram-dataset.csv"))
 
     # file names on train_dir
     files = os.listdir(train_dir)
@@ -142,7 +144,6 @@ def getFiles():
                 rta.append((file_name, lower[0], upper[0]))
             else:
                 Console.log("Not data for", file_name)
-                files.remove(file_name)
 
     return rta
 
@@ -406,3 +407,6 @@ if __name__ == "__main__":
                 Console.error("File %s, Lower: %s, Upper: %s" % (files[i], lower, upper))
             else:
                 Console.log("File %s, Lower: %s, Upper: %s" % (name, lower, upper))
+
+    if args["predict"] != None:
+        print(args["predict"])

### 2018-08-11 deep_cut_hands.py
Improve console log

@@ -39,18 +39,14 @@ SORT_RANDOMLY = True
 
 # construct the argument parse and parse the arguments
 ap = argparse.ArgumentParser()
-ap.add_argument("-lw", "--load_weights",
-                help="Path to the file weights")
-ap.add_argument("-tb", "--tensorBoard", default=False,
-                help="Active tensorBoard")
-ap.add_argument("-rl", "--reduce_learning", default=False,
-                help="Active reduce learning rate")
-ap.add_argument("-cp", "--checkpoint", default=True,
-                help="Active checkpoint")
-ap.add_argument("-t", "--train", default=True,
-                help="Run train model")
-ap.add_argument("-p", "--predict",
-                help="File to predict values")
+ap.add_argument("-lw", "--load_weights", help="Path to the file weights")
+ap.add_argument("-tb", "--tensorBoard", default=False, help="Active tensorBoard")
+ap.add_argument(
+    "-rl", "--reduce_learning", default=False, help="Active reduce learning rate"
+)
+ap.add_argument("-cp", "--checkpoint", default=True, help="Active checkpoint")
+ap.add_argument("-t", "--train", default=True, help="Run train model")
+ap.add_argument("-p", "--predict", help="File to predict values")
 args = vars(ap.parse_args())
 
 # For this problem the validation and test data provided by the concerned authority did not have labels,
@@ -140,7 +136,7 @@ def getFiles():
             lower = csv_row.lower.tolist()
             # Get upper color
             upper = csv_row.upper.tolist()
-            if not(lower[0] != lower[0] and upper[0] != upper[0]):
+            if not (lower[0] != lower[0] and upper[0] != upper[0]):
                 rta.append((file_name, lower[0], upper[0]))
             else:
                 Console.log("Not data for", file_name)
@@ -207,17 +203,17 @@ def makerModel():
 
     x_lower = Dense(256, activation="sigmoid")(hist_input)
     x_lower = Dense(256, activation="relu")(x_lower)
-    #x_lower = Dense(200, activation="relu")(x_lower)
+    # x_lower = Dense(200, activation="relu")(x_lower)
     x_lower = Dense(128, activation="relu")(x_lower)
[…]

### 2018-08-11 deep_cut_hands.py
Add new argument

@@ -41,11 +41,13 @@ SORT_RANDOMLY = True
 ap = argparse.ArgumentParser()
 ap.add_argument("-lw", "--load_weights", help="Path to the file weights")
 ap.add_argument("-tb", "--tensorBoard", default=False, help="Active tensorBoard")
+ap.add_argument("-cp", "--checkpoint", default=True, help="Active checkpoint")
 ap.add_argument(
     "-rl", "--reduce_learning", default=False, help="Active reduce learning rate"
 )
-ap.add_argument("-cp", "--checkpoint", default=True, help="Active checkpoint")
+
 ap.add_argument("-t", "--train", default=True, help="Run train model")
+ap.add_argument("-e", "--evaluate", default=True, help="Evaluating model")
 ap.add_argument("-p", "--predict", help="File to predict values")
 args = vars(ap.parse_args())
 
@@ -375,40 +377,53 @@ class Console(object):
 # Este if permite que solo se ejecute lo que sigue si es llamado
 # como proceso raíz.
 if __name__ == "__main__":
+    # Check if exixt folder
     checkPath()
+    # Create model
+    model = makerModel()
 
     files = getFiles()
     (X_train, y_lower, y_upper) = loadDataSet(files)
 
-    model = makerModel()
     if args["train"] == True:
         trainModel(model, X_train, y_lower, y_upper)
     else:
-        Console.info("Predict...")
-        # new instance where we do not know the answer
-        Xnew = X_train
-        Xnew = np.array(Xnew)
-        # make a prediction
-        ynew = model.predict(Xnew)
+        if args["evaluate"] == True:
+            Console.info("Evaluating model...")
+            score = model.evaluate(
+                [X_train], [y_lower, y_upper], batch_size=BATCH_SIZE, verbose=1
+            )
+            Console.log("Test loss:", score[1], score[4])
+            Console.log("Test MAE:", score[3], score[5])
+            Console.log("Test MSE:", score[0], score[2])
+        else:
+            Console.info("Predict...")
+            # new instance where we do not know the answer
+            Xnew = X_train
+            Xnew = np.array(Xnew)
 
-        for i in range(len(files)):
-            (name, x_lower, x_upper) = files[i]
-            lower = int(ynew[0][i])
-            upper = int(ynew[1][i])
-            e_lower = x_lower - lower
-            e_upper = x_upper - upper
+            # make a prediction
+            ynew = model.predict(Xnew)
 
[…]

### 2018-08-11 deep_cut_hands.py
Fix using argument

@@ -40,14 +40,14 @@ SORT_RANDOMLY = True
 # construct the argument parse and parse the arguments
 ap = argparse.ArgumentParser()
 ap.add_argument("-lw", "--load_weights", help="Path to the file weights")
-ap.add_argument("-tb", "--tensorBoard", default=False, help="Active tensorBoard")
-ap.add_argument("-cp", "--checkpoint", default=True, help="Active checkpoint")
+ap.add_argument("-tb", "--tensorBoard", default='False', help="Active tensorBoard")
+ap.add_argument("-cp", "--checkpoint", default='True', help="Active checkpoint")
 ap.add_argument(
-    "-rl", "--reduce_learning", default=False, help="Active reduce learning rate"
+    "-rl", "--reduce_learning", default='False', help="Active reduce learning rate"
 )
 
-ap.add_argument("-t", "--train", default=True, help="Run train model")
-ap.add_argument("-e", "--evaluate", default=True, help="Evaluating model")
+ap.add_argument("-t", "--train", default='True', help="Run train model")
+ap.add_argument("-e", "--evaluate", default='False', help="Evaluating model")
 ap.add_argument("-p", "--predict", help="File to predict values")
 args = vars(ap.parse_args())
 
@@ -189,11 +189,11 @@ def loadCallBack():
 
     cb = []
 
-    if args["tensorBoard"] == True:
+    if args["tensorBoard"] == 'True':
         cb.append(tbCallBack)
-    if args["checkpoint"] == True:
+    if args["checkpoint"] == 'True':
         cb.append(checkpoint)
-    if args["reduce_learning"] == True:
+    if args["reduce_learning"] == 'True':
         cb.append(reduceLROnPlat)
 
     return cb
@@ -379,16 +379,20 @@ class Console(object):
 if __name__ == "__main__":
     # Check if exixt folder
     checkPath()
+
+    if args["predict"] != None and args["train"] == 'False':
+        Console.info("Predict for", args["predict"])
+    else:
+        files = getFiles()
+        (X_train, y_lower, y_upper) = loadDataSet(files)
+
     # Create model
     model = makerModel()
 
-    files = getFiles()
-    (X_train, y_lower, y_upper) = loadDataSet(files)
-
-    if args["train"] == True:
+    if args["train"] == 'True' and args["evaluate"] == 'False':
         trainModel(model, X_train, y_lower, y_upper)
     else:
-        if args["evaluate"] == True:
+        if args["evaluate"] == 'True':
[…]

### 2018-08-11 deep_cut_hands.py
Fix using arguments

@@ -1,6 +1,8 @@
 #!/usr/bin/python3
 # ./deep_cut_hands.py -lw ./model-backup/cut-hand/model.h5
 # ./deep_cut_hands.py --train False -lw ./model-backup/cut-hand/model.h5
+# ./deep_cut_hands.py -lw ./model-backup/cut-hand/model.h5 --train False --evaluate True --predict True
+
 
 from keras.applications import InceptionV3, ResNet50, Xception
 from keras.layers import Flatten, Dense, Input, Dropout
@@ -380,26 +382,28 @@ if __name__ == "__main__":
     # Check if exixt folder
     checkPath()
 
-    if args["predict"] != None and args["train"] == 'False':
-        Console.info("Predict for", args["predict"])
-    else:
+    if args["predict"] == None or args['predict'] == 'True':
         files = getFiles()
         (X_train, y_lower, y_upper) = loadDataSet(files)
 
     # Create model
     model = makerModel()
 
-    if args["train"] == 'True' and args["evaluate"] == 'False':
+    if args["train"] == 'True':
         trainModel(model, X_train, y_lower, y_upper)
-    else:
-        if args["evaluate"] == 'True':
-            Console.info("Evaluating model...")
-            score = model.evaluate(
-                [X_train], [y_lower, y_upper], batch_size=BATCH_SIZE, verbose=1
-            )
-            Console.log("Test loss:", score[1], score[4])
-            Console.log("Test MAE:", score[3], score[5])
-            Console.log("Test MSE:", score[0], score[2])
+
+    if args["evaluate"] == 'True':
+        Console.info("Evaluating model...")
+        score = model.evaluate(
+            [X_train], [y_lower, y_upper], batch_size=BATCH_SIZE, verbose=1
+        )
+        Console.log("Test loss:", score[1], score[4])
+        Console.log("Test MAE:", score[3], score[5])
+        Console.log("Test MSE:", score[0], score[2])
+
+    if args["predict"] != None and args['predict'] != 'False':
+        if args["predict"] != 'True':
+            Console.info("Predict for", args["predict"])
         else:
             Console.info("Predict...")
             # new instance where we do not know the answer

### 2018-08-11 deep_cut_hands.py
Fix train data

@@ -36,6 +36,9 @@ BATCH_SIZE = 1
 OPTIMIZER = Adadelta(lr=1.0, rho=0.95, epsilon=None, decay=0.0)
 # OPTIMIZER = Adagrad(lr=0.05)
 
+# Show how it closed when the difference is N color
+E_TOLERANCE = 20
+
 # Sort dataset randomly
 SORT_RANDOMLY = True
 
@@ -420,9 +423,8 @@ if __name__ == "__main__":
                 e_lower = x_lower - lower
                 e_upper = x_upper - upper
 
-                e_tolerance = 10
-                e_lower = e_lower > e_tolerance or e_lower < -e_tolerance
-                e_upper = e_upper > e_tolerance or e_upper < -e_tolerance
+                e_lower = e_lower > E_TOLERANCE or e_lower < -E_TOLERANCE
+                e_upper = e_upper > E_TOLERANCE or e_upper < -E_TOLERANCE
 
                 if e_lower or e_upper:
                     lower = Console.Red + str(lower) + Console.NC if e_lower else lower

### 2018-08-11 deep_cut_hands.py
mae-6.2-16.5

@@ -28,12 +28,12 @@ CUT_DATASET = 1000
 
 # network and training
 EPOCHS = 500
-BATCH_SIZE = 1
+BATCH_SIZE = 35
 
 # https://keras.io/optimizers
-# OPTIMIZER = Adam(lr=0.001)
+OPTIMIZER = Adam(lr=0.001)
 # OPTIMIZER = RMSprop()
-OPTIMIZER = Adadelta(lr=1.0, rho=0.95, epsilon=None, decay=0.0)
+# OPTIMIZER = Adadelta(lr=0.01, rho=0.95, epsilon=None, decay=0.0)
 # OPTIMIZER = Adagrad(lr=0.05)
 
 # Show how it closed when the difference is N color

### 2018-08-12 deep_cut_hands.py
Cleaner code, update train dataset

@@ -3,12 +3,9 @@
 # ./deep_cut_hands.py --train False -lw ./model-backup/cut-hand/model.h5
 # ./deep_cut_hands.py -lw ./model-backup/cut-hand/model.h5 --train False --evaluate True --predict True
 
-
-from keras.applications import InceptionV3, ResNet50, Xception
-from keras.layers import Flatten, Dense, Input, Dropout
-from keras.models import Model, Sequential
+from keras.layers import Flatten, Dense, Input, Dropout, BatchNormalization
+from keras.models import Model
 from keras.optimizers import Adam, RMSprop, Adadelta, Adagrad
-from six.moves import cPickle
 import argparse
 import cv2
 import fnmatch
@@ -27,8 +24,8 @@ TRAIN_DIR = "dataset_sample"
 CUT_DATASET = 1000
 
 # network and training
-EPOCHS = 500
-BATCH_SIZE = 35
+EPOCHS = 600
+BATCH_SIZE = 24
 
 # https://keras.io/optimizers
 OPTIMIZER = Adam(lr=0.001)
@@ -78,12 +75,7 @@ def writeImage(path, image, force=False):
         cv2.imwrite(os.path.join(__location__, TRAIN_DIR, path, img_file), image)
 
 
-def processImage(img_path):
-    # Read a image
-    img = cv2.imread(img_path)
-
-    img = cv2.cvtColor(img, cv2.COLOR_BGR2GRAY)
-
+def getHistogram(img):
     hist, _ = np.histogram(img, 256, [0, 256])
 
     cdf = hist.cumsum()
@@ -108,8 +100,11 @@ def loadDataSet(files=[]):
 
         # Get image's path
         img_path = os.path.join(train_dir, img_file)
+        # Read a image
+        img = cv2.imread(img_path, 0)
+        # img = cv2.cvtColor(img, cv2.COLOR_BGR2GRAY)
 
-        X_train.append(processImage(img_path))
+        X_train.append(getHistogram(img))
         y_lower.append(lower)
         y_upper.append(upper)
 
@@ -210,6 +205,7 @@ def makerModel():
 
     x_lower = Dense(256, activation="sigmoid")(hist_input)
     x_lower = Dense(256, activation="relu")(x_lower)
+    # x_lower = BatchNormalization(mode=0, axis=1)(x_lower)
     # x_lower = Dense(200, activation="relu")(x_lower)
     x_lower = Dense(128, activation="relu")(x_lower)
[…]

### 2018-08-12 deep_cut_hands.py
Correct color histogram with deep learning

@@ -227,8 +227,9 @@ def makerModel():
 
     model.compile(loss="mean_squared_error", metrics=["MAE", "MSE"], optimizer=OPTIMIZER)
 
-    Console.info("Model summary")
-    print(model.summary())
+    if __name__ == "__main__":
+        Console.info("Model summary")
+        print(model.summary())
 
     # Load weight
     if args["load_weights"] != None:

### 2018-08-12 pickle_dataset.py

@@ -1,5 +1,6 @@
 #!/usr/bin/python3
 
+from deep_cut_hands import makerModel, getHistogram
 from six.moves import cPickle
 import cv2
 import fnmatch
@@ -35,6 +36,9 @@ SAVE_IMAGE_FOR_DEBUGGER = False
 # Simple dataset is correct, I am verifying the original.
 EXTRACTING_HANDS = True
 
+# Using deep learning for normalizing histogram of level colors
+IA_EXTRACTING_HANDS = True
+
 # Turn rotate image on/off
 ROTATE_IMAGE = True
 
@@ -46,8 +50,12 @@ train_dir = os.path.join(__location__, TRAIN_DIR)
 
 img_file = ""
 
+# Save model
+deep_model = None
 
 # Show the images
+
+
 def writeImage(path, image, force=False):
     if SAVE_IMAGE_FOR_DEBUGGER or force:
         cv2.imwrite(os.path.join(__location__, TRAIN_DIR, path, img_file), image)
@@ -60,10 +68,20 @@ def writeImage(path, image, force=False):
 def histogramsLevelFix(img):
     # This function is only prepared for images in scale of gripes
     img = cv2.cvtColor(img, cv2.COLOR_BGR2GRAY)
-    # Find the acceptable limits of the intensity histogram
-    min_color, max_color = np.percentile(img, (2.5, 99.4))
-    min_color = int(min_color)
-    max_color = int(max_color)
+
+    if IA_EXTRACTING_HANDS == True:
+        X_img = getHistogram(img)
+        X_new = np.array([X_img])
+
+        predict = deep_model.predict(X_new)
+        min_color = int(predict[0][0])
+        max_color = int(predict[1][0])
+        # print("Lower: %s, Upper: %s" % (min_color, max_color))
+    else:
+        # Find the acceptable limits of the intensity histogram
+        min_color, max_color = np.percentile(img, (2.5, 99.4))
+        min_color = int(min_color)
+        max_color = int(max_color)
 
     # To improve the preform we created a color palette with the new values
     colors_palette = []
@@ -238,10 +256,20 @@ def processImage(img_path):
 
 
 def loadDataSet(files=[]):
+    global deep_model
     global img_file
     X_train = []
     y_age = []
     y_gender = []
+
+    if IA_EXTRACTING_HANDS == True:
+        deep_model = makerModel()
+        try:
+            deep_model.load_weights(os.path.join(
+                __location__, "model-backup", "cut-hand", "model.h5"))
[…]

### 2018-08-12 deep_cut_hand/main_histogram.py
New folder structure

@@ -1,7 +1,7 @@
 #!/usr/bin/python3
-# ./deep_cut_hands.py -lw ./model-backup/cut-hand/model.h5
-# ./deep_cut_hands.py --train False -lw ./model-backup/cut-hand/model.h5
-# ./deep_cut_hands.py -lw ./model-backup/cut-hand/model.h5 --train False --evaluate True --predict True
+# ./main_histogram.py -lw ./model/model_histogram.h5
+# ./main_histogram.py -lw ./model/model_histogram.h5 --train False
+# ./main_histogram.py -lw ./model/model_histogram.h5 --train False --evaluate True --predict True
 
 from keras.layers import Flatten, Dense, Input, Dropout, BatchNormalization
 from keras.models import Model
@@ -57,7 +57,7 @@ args = vars(ap.parse_args())
 # so the training data was split into train, test and validation sets
 __location__ = os.path.realpath(os.path.join(os.getcwd(), os.path.dirname(__file__)))
 
-train_dir = os.path.join(__location__, TRAIN_DIR)
+train_dir = os.path.join(__location__, '..', TRAIN_DIR)
 
 img_file = ""
 
@@ -147,53 +147,59 @@ def getFiles():
 
 
 # Create the directories to save the images
-def checkPath():
-    if SAVE_IMAGE_FOR_DEBUGGER:
-        for folder in ["histograms_level_fix", "cut_hand", "render", "mask"]:
-            if not os.path.exists(os.path.join(__location__, TRAIN_DIR, folder)):
-                Console.info("Create folder", folder)
-                os.makedirs(os.path.join(__location__, TRAIN_DIR, folder))
-    if SAVE_RENDERS:
-        if not os.path.exists(os.path.join(__location__, TRAIN_DIR, "render")):
-            Console.info("Create folder render")
-            os.makedirs(os.path.join(__location__, TRAIN_DIR, "render"))
+# def checkPath():
+#    if SAVE_IMAGE_FOR_DEBUGGER:
+#        for folder in ["histograms_level_fix", "cut_hand", "render", "mask"]:
+#            if not os.path.exists(os.path.join(__location__, TRAIN_DIR, folder)):
+#                Console.info("Create folder", folder)
+#                os.makedirs(os.path.join(__location__, TRAIN_DIR, folder))
+#    if SAVE_RENDERS:
+#        if not os.path.exists(os.path.join(__location__, TRAIN_DIR, "render")):
[…]

### 2018-08-12 pickle_dataset.py

@@ -1,6 +1,6 @@
 #!/usr/bin/python3
 
-from deep_cut_hands import makerModel, getHistogram
+from deep_cut_hand.main_histogram import makerModel, getHistogram
 from six.moves import cPickle
 import cv2
 import fnmatch
@@ -30,7 +30,7 @@ SAVE_RENDERS = False
 
 # Create intermediate images in separate folders for debugger.
 # mask, cut_hand, delete_object, render
-SAVE_IMAGE_FOR_DEBUGGER = False
+SAVE_IMAGE_FOR_DEBUGGER = not False
 
 # Extracting hands from images and using that new dataset.
 # Simple dataset is correct, I am verifying the original.
@@ -40,7 +40,7 @@ EXTRACTING_HANDS = True
 IA_EXTRACTING_HANDS = True
 
 # Turn rotate image on/off
-ROTATE_IMAGE = True
+ROTATE_IMAGE = False
 
 # For this problem the validation and test data provided by the concerned authority did not have labels,
 # so the training data was split into train, test and validation sets
@@ -266,7 +266,7 @@ def loadDataSet(files=[]):
         deep_model = makerModel()
         try:
             deep_model.load_weights(os.path.join(
-                __location__, "model-backup", "cut-hand", "model.h5"))
+                __location__, "deep_cut_hand", "model", "model_histogram.h5"))
         except:
             print("I can not find the weights for the model.")
             exit(0)

### 2018-08-12 pickle_dataset.py
Fix color range

@@ -26,11 +26,11 @@ SPLIT_GENDER = 'both'
 # SPLIT_GENDER = 'male'
 
 # Turn saving renders feature on/off
-SAVE_RENDERS = False
+SAVE_RENDERS = not False
 
 # Create intermediate images in separate folders for debugger.
 # mask, cut_hand, delete_object, render
-SAVE_IMAGE_FOR_DEBUGGER = not False
+SAVE_IMAGE_FOR_DEBUGGER = False
 
 # Extracting hands from images and using that new dataset.
 # Simple dataset is correct, I am verifying the original.
@@ -53,9 +53,8 @@ img_file = ""
 # Save model
 deep_model = None
 
+
 # Show the images
-
-
 def writeImage(path, image, force=False):
     if SAVE_IMAGE_FOR_DEBUGGER or force:
         cv2.imwrite(os.path.join(__location__, TRAIN_DIR, path, img_file), image)
@@ -76,6 +75,8 @@ def histogramsLevelFix(img):
         predict = deep_model.predict(X_new)
         min_color = int(predict[0][0])
         max_color = int(predict[1][0])
+        min_color = min_color if min_color > 0 else 0
+        max_color = max_color if max_color < 255 else 255
         # print("Lower: %s, Upper: %s" % (min_color, max_color))
     else:
         # Find the acceptable limits of the intensity histogram

### 2018-08-12 main.py
Using module code

@@ -21,7 +21,7 @@ __location__ = os.path.realpath(os.path.join(os.getcwd(), os.path.dirname(__file
 
 # network and training
 EPOCHS = 30
-BATCH_SIZE = 25
+BATCH_SIZE = 35
 VERBOSE = 1
 # https://keras.io/optimizers
 OPTIMIZER = Adam(lr=0.001)

### 2018-08-12 pickle_dataset.py

@@ -64,25 +64,9 @@ def writeImage(path, image, force=False):
 # We order the colors of the image with their frequency and
 # obtain the accumulated one, then we obtain the colors that
 # accumulate 2.5% and 99.4% of the frequency.
-def histogramsLevelFix(img):
+def histogramsLevelFix(img, min_color, max_color):
     # This function is only prepared for images in scale of gripes
-    img = cv2.cvtColor(img, cv2.COLOR_BGR2GRAY)
-
-    if IA_EXTRACTING_HANDS == True:
-        X_img = getHistogram(img)
-        X_new = np.array([X_img])
-
-        predict = deep_model.predict(X_new)
-        min_color = int(predict[0][0])
-        max_color = int(predict[1][0])
-        min_color = min_color if min_color > 0 else 0
-        max_color = max_color if max_color < 255 else 255
-        # print("Lower: %s, Upper: %s" % (min_color, max_color))
-    else:
-        # Find the acceptable limits of the intensity histogram
-        min_color, max_color = np.percentile(img, (2.5, 99.4))
-        min_color = int(min_color)
-        max_color = int(max_color)
+    # img = cv2.cvtColor(img, cv2.COLOR_BGR2GRAY)
 
     # To improve the preform we created a color palette with the new values
     colors_palette = []
@@ -228,12 +212,33 @@ def updateProgress(progress, tick="", total="", status="Loading..."):
     sys.stdout.flush()
 
 
+def getColorsHands(img):
+    if IA_EXTRACTING_HANDS == True:
+        X_img = getHistogram(img)
+        X_new = np.array([X_img])
+
+        predict = deep_model.predict(X_new)
+        min_color = int(predict[0][0])
+        max_color = int(predict[1][0])
+        min_color = min_color if min_color > 0 else 0
+        max_color = max_color if max_color < 255 else 255
+        # print("Lower: %s, Upper: %s" % (min_color, max_color))
+    else:
+        # Find the acceptable limits of the intensity histogram
+        min_color, max_color = np.percentile(img, (2.5, 99.4))
+        min_color = int(min_color)
+        max_color = int(max_color)
+
+    return (min_color, max_color)
+
+
 def processImage(img_path):
     # Read a image
-    img = cv2.imread(img_path)
+    img = cv2.imread(img_path, 0)
 
     # Adjust color levels
-    img = histogramsLevelFix(img)
+    min_color, max_color = getColorsHands(img)
[…]

### 2018-08-23 deep_cut_hand/learn_get_hand_histogram.py
Fix for adam optimizer

@@ -29,7 +29,7 @@ EPOCHS = 1500
 BATCH_SIZE = 17
 
 # https://keras.io/optimizers
-OPTIMIZER = Adam(lr=0.001)
+OPTIMIZER = Adam(lr=0.001, amsgrad=True)
 # OPTIMIZER = RMSprop()
 # OPTIMIZER = Adadelta(lr=0.01, rho=0.95, epsilon=None, decay=0.0)
 # OPTIMIZER = Adagrad(lr=0.05)

### 2018-08-23 deep_cut_hand/learn_to_recognize_hands.py

@@ -21,8 +21,8 @@ EPOCHS = 150
 BATCH_SIZE = 7
 
 # https://keras.io/optimizers
-# OPT = Adam(lr=0.001)
-OPT = RMSprop()
+OPT = Adam(lr=0.001, amsgrad=True)
+# OPT = RMSprop()
 # OPT = SGD(lr=0.01, clipvalue=0.5)
 # OPT = Adadelta(lr=0.01, rho=0.95, epsilon=None, decay=0.0)
 # OPT = Adagrad(lr=0.05)

### 2018-08-24 deep_cut_hand/learn_to_recognize_hands.py
Add learning rate scheduler

@@ -5,32 +5,34 @@
 --evaluate True
 --predict True
 """
+from get_hands_dataset import openDataSet
+from keras.callbacks import LearningRateScheduler
 from keras.layers import Flatten, Dense, Input, Dropout, BatchNormalization, concatenate
 from keras.models import Model, Sequential
 from keras.optimizers import Adam, RMSprop, Adadelta, Adagrad, SGD
 from utilities import Console, updateProgress
-from get_hands_dataset import openDataSet
-import math
 import argparse
 import keras
+import math
 import numpy as np
 import os
 
 # network and training
 EPOCHS = 150
-BATCH_SIZE = 7
+BATCH_SIZE = 5
 
 # https://keras.io/optimizers
 OPT = Adam(lr=0.001, amsgrad=True)
 # OPT = RMSprop()
-# OPT = SGD(lr=0.01, clipvalue=0.5)
+# OPT = SGD(lr=0.01, decay=0.01 / EPOCHS, momentum=0.9, nesterov=True)
 # OPT = Adadelta(lr=0.01, rho=0.95, epsilon=None, decay=0.0)
 # OPT = Adagrad(lr=0.05)
 
 # construct the argument parse and parse the arguments
 ap = argparse.ArgumentParser()
 ap.add_argument("-lw", "--load_weights", help="Path to the file weights")
-ap.add_argument("-tb", "--tensorBoard", default="False", help="Active tensorBoard")
+ap.add_argument("-sd", "--stepDecay", default="False", help="Active step decay")
+ap.add_argument("-tb", "--tensorBoard", default="False", help="Active tensor board")
 ap.add_argument("-cp", "--checkpoint", default="False", help="Active checkpoint")
 ap.add_argument(
     "-rl", "--reduce_learning", default="True", help="Active reduce learning rate"
@@ -55,6 +57,19 @@ SAVE_IMAGE_FOR_DEBUGGER = False
 # Make Keras callback
 def loadCallBack():
     cb = []
+
+    if args["stepDecay"] == "True":
+        def stepDecay(epoch):
+            # initialize the base initial learning rate, drop factor, and epochs to drop every
+            initAlpha = 0.01
+            # factor = 0.25
+            factor = 0.5
+            dropEvery = 5
+            # compute learning rate for the current epoch
+            alpha = initAlpha * (factor ** np.floor((1 + epoch) / dropEvery))
+            # return the learning rate
+            return float(alpha)
[…]

### 2018-08-24 main_no_gender.py
adding csvlogger callback and amsgrad option to optimizer

@@ -25,11 +25,11 @@ GENDER_TYPE = "famale"
 # GENDER_TYPE = "male"
 
 # network and training
-EPOCHS = 30
+EPOCHS = 1
 BATCH_SIZE = 32
 VERBOSE = 1
 # https://keras.io/optimizers
-OPTIMIZER = Adam(lr=0.001)
+OPTIMIZER = Adam(lr=0.001, amsgrad=True)
 # OPTIMIZER = RMSprop()
 # OPTIMIZER = Adadelta(lr=1.0, rho=0.95, epsilon=None, decay=0.0)
 # OPTIMIZER = Adagrad(lr=0.05)
@@ -153,6 +153,16 @@ tbCallBack = keras.callbacks.TensorBoard(
 )
 print("tensorboard --logdir", LOG_DIR_TENSORBOARD)
 
+# Path to save model
+PATH_SAVE_MODEL = os.path.join(__location__, "model_backup", GENDER_TYPE)
+
+# Save weights after every epoch
+if not os.path.exists(PATH_SAVE_MODEL):
+    os.makedirs(PATH_SAVE_MODEL)
+
+csv_logger = keras.callbacks.CSVLogger(os.path.join(__location__, "model_backup", "training.csv"))
+
+
 history = model.fit(
     [img_train],
     [age_train],
@@ -160,16 +170,11 @@ history = model.fit(
     epochs=EPOCHS,
     verbose=VERBOSE,
     validation_data=([img_valid], [age_valid]),
-    callbacks=[tbCallBack, checkpoint, reduceLROnPlat],
+    callbacks=[tbCallBack, checkpoint, reduceLROnPlat, csv_logger],
     #     callbacks=[tbCallBack, checkpoint],
 )
 
-# Path to save model
-PATH_SAVE_MODEL = os.path.join(__location__, "model_backup", GENDER_TYPE)
 
-# Save weights after every epoch
-if not os.path.exists(PATH_SAVE_MODEL):
-    os.makedirs(PATH_SAVE_MODEL)
 
 # serialize model to YAML
 model_yaml = model.to_yaml()

### 2018-08-24 main_no_gender.py
fix, forgot gender and changed back epochs

@@ -25,7 +25,7 @@ GENDER_TYPE = "famale"
 # GENDER_TYPE = "male"
 
 # network and training
-EPOCHS = 1
+EPOCHS = 30
 BATCH_SIZE = 32
 VERBOSE = 1
 # https://keras.io/optimizers
@@ -160,7 +160,7 @@ PATH_SAVE_MODEL = os.path.join(__location__, "model_backup", GENDER_TYPE)
 if not os.path.exists(PATH_SAVE_MODEL):
     os.makedirs(PATH_SAVE_MODEL)
 
-csv_logger = keras.callbacks.CSVLogger(os.path.join(__location__, "model_backup", "training.csv"))
+csv_logger = keras.callbacks.CSVLogger(os.path.join(__location__, "model_backup", GENDER_TYPE, "training.csv"))
 
 
 history = model.fit(

### 2018-08-24 main.py
Save csv log using PATH_SAVE_MODEL

@@ -207,7 +207,7 @@ PATH_SAVE_MODEL = os.path.join(__location__, "model_backup", "famale_and_male")
 if not os.path.exists(PATH_SAVE_MODEL):
     os.makedirs(PATH_SAVE_MODEL)
 
-csv_logger = keras.callbacks.CSVLogger(os.path.join(__location__, "model_backup", "famale_and_male", "training.csv"))
+csv_logger = keras.callbacks.CSVLogger(os.path.join(PATH_SAVE_MODEL, "training.csv"))
 
 history = model.fit(
     [img_train, gdr_train],

### 2018-08-24 main_no_gender.py

@@ -160,8 +160,7 @@ PATH_SAVE_MODEL = os.path.join(__location__, "model_backup", GENDER_TYPE)
 if not os.path.exists(PATH_SAVE_MODEL):
     os.makedirs(PATH_SAVE_MODEL)
 
-csv_logger = keras.callbacks.CSVLogger(os.path.join(__location__, "model_backup", GENDER_TYPE, "training.csv"))
-
+csv_logger = keras.callbacks.CSVLogger(os.path.join(PATH_SAVE_MODEL, "training.csv"))
 
 history = model.fit(
     [img_train],
@@ -173,7 +172,6 @@ history = model.fit(
     callbacks=[tbCallBack, checkpoint, reduceLROnPlat, csv_logger],
     #     callbacks=[tbCallBack, checkpoint],
 )
-
 
 
 # serialize model to YAML

### 2018-08-25 deep_cut_hand/learn_get_hand_histogram.py
Add new callback

@@ -1,6 +1,6 @@
 #!/usr/bin/python3
 """
-./learn_get_hand_histogram.py -lw ./model/model_histogram.h5
+./learn_get_hand_histogram.py lw ./model/model_histogram.h5
 --train True
 --evaluate True
 --predict True
@@ -8,6 +8,7 @@
 from keras.layers import Flatten, Dense, Input, Dropout, BatchNormalization, concatenate
 from keras.models import Model
 from keras.optimizers import Adam, RMSprop, Adadelta, Adagrad
+from keras.utils import plot_model, print_summary
 from utilities import Console, updateProgress, getHistogram
 import argparse
 import cv2
@@ -42,7 +43,7 @@ SORT_RANDOMLY = True
 
 # construct the argument parse and parse the arguments
 ap = argparse.ArgumentParser()
-ap.add_argument("-lw", "--load_weights", help="Path to the file weights")
+ap.add_argument("-w", "--weights", help="Path to the file weights")
 ap.add_argument("-tb", "--tensorBoard", default="False", help="Active tensorBoard")
 ap.add_argument("-cp", "--checkpoint", default="False", help="Active checkpoint")
 ap.add_argument(
@@ -169,8 +170,10 @@ def loadCallBack():
             os.makedirs(os.path.join(__location__, "weights"))
         checkpoint = keras.callbacks.ModelCheckpoint(
             filepath="weights/weights.{epoch:02d}-{val_loss:.2f}.hdf5",
+            monitor='val_loss',
+            verbose=1,
             save_weights_only=True,
-            period=1,
+            period=1
         )
         Console.info("Save weights after every epoch")
         cb.append(checkpoint)
@@ -225,9 +228,10 @@ def makerModel():
         print(model.summary())
 
     # Load weight
-    if args["load_weights"] != None:
-        Console.info("Loading weights from", args["load_weights"])
-        model.load_weights(args["load_weights"])
+    load_weights = args["weights"]
+    if load_weights != None:
+        Console.info("Loading weights from", load_weights)
+        model.load_weights(load_weights)
 
     return model
 
@@ -285,6 +289,8 @@ def trainModel(model, X_train, y_lower, y_upper):
         yaml_file.write(model_yaml)
     # serialize weights to HDF5
     model.save_weights(os.path.join(PATHE_SAVE_MODEL, "model_histogram.h5"))
+    # save image of build model
+    plot_model(model, to_file="model_histogram.png", show_shapes=True)
     print("OK")
 
     # evaluate the network

### 2018-08-25 deep_cut_hand/learn_to_recognize_hands.py

@@ -1,6 +1,6 @@
 #!/usr/bin/python3
 """
-./learn_to_recognize_hands.py -lw ./model/model_hands_not_hands.h5
+./learn_to_recognize_hands.py -w ./model/model_hands_not_hands.h5
 --train True
 --evaluate True
 --predict True
@@ -10,6 +10,7 @@ from keras.callbacks import LearningRateScheduler
 from keras.layers import Flatten, Dense, Input, Dropout, BatchNormalization, concatenate
 from keras.models import Model, Sequential
 from keras.optimizers import Adam, RMSprop, Adadelta, Adagrad, SGD
+from keras.utils import plot_model, print_summary
 from utilities import Console, updateProgress
 import argparse
 import keras
@@ -30,7 +31,7 @@ OPT = Adam(lr=0.001, amsgrad=True)
 
 # construct the argument parse and parse the arguments
 ap = argparse.ArgumentParser()
-ap.add_argument("-lw", "--load_weights", help="Path to the file weights")
+ap.add_argument("-w", "--weights", help="Path to the file weights")
 ap.add_argument("-sd", "--stepDecay", default="False", help="Active step decay")
 ap.add_argument("-tb", "--tensorBoard", default="False", help="Active tensor board")
 ap.add_argument("-cp", "--checkpoint", default="False", help="Active checkpoint")
@@ -96,8 +97,10 @@ def loadCallBack():
             os.makedirs(os.path.join(__location__, "weights"))
         checkpoint = keras.callbacks.ModelCheckpoint(
             filepath="weights/weights.{epoch:02d}-{val_loss:.2f}.hdf5",
+            monitor='val_loss',
+            verbose=1,
             save_weights_only=True,
-            period=1,
+            period=1
         )
         Console.info("Save weights after every epoch")
         cb.append(checkpoint)
@@ -142,9 +145,10 @@ def makerModel():
         print(model.summary())
 
     # Load weight
-    if args["load_weights"] != None:
-        Console.info("Loading weights from", args["load_weights"])
-        model.load_weights(args["load_weights"])
+    load_weights = args["weights"]
+    if load_weights != None:
+        Console.info("Loading weights from", load_weights)
+        model.load_weights(load_weights)
 
     return model
 
@@ -190,6 +194,8 @@ def trainModel(model, X_train, y_train):
         yaml_file.write(model_yaml)
     # serialize weights to HDF5
[…]

### 2018-08-25 deep_cut_hand/learn_get_hand_histogram.py
Fix

@@ -1,6 +1,6 @@
 #!/usr/bin/python3
 """
-./learn_get_hand_histogram.py lw ./model/model_histogram.h5
+./learn_get_hand_histogram.py -w ./model/model_histogram.h5
 --train True
 --evaluate True
 --predict True

### 2018-08-25 deep_cut_hand/learn_get_hand_histogram.py
Fix same deep_cut_hands model

@@ -290,7 +290,11 @@ def trainModel(model, X_train, y_lower, y_upper):
     # serialize weights to HDF5
     model.save_weights(os.path.join(PATHE_SAVE_MODEL, "model_histogram.h5"))
     # save image of build model
-    plot_model(model, to_file="model_histogram.png", show_shapes=True)
+    plot_model(
+        model,
+        to_file=os.path.join(PATHE_SAVE_MODEL, "model_histogram.png"),
+        show_shapes=True
+    )
     print("OK")
 
     # evaluate the network

### 2018-08-25 deep_cut_hand/learn_to_recognize_hands.py

@@ -195,7 +195,12 @@ def trainModel(model, X_train, y_train):
     # serialize weights to HDF5
     model.save_weights(os.path.join(PATHE_SAVE_MODEL, "model_hands_not_hands.h5"))
     # save image of build model
-    plot_model(model, to_file="model_hands_not_hands.png", show_shapes=True)
+    # save image of build model
+    plot_model(
+        model,
+        to_file=os.path.join(PATHE_SAVE_MODEL, "model_hands_not_hands.png"),
+        show_shapes=True
+    )
     print("OK")
 
     # evaluate the network

### 2018-08-25 paper/paper.tex
adding bibliography references and created folder for external files used

--- 2018-08-08 paper/paper.tex
@@
 
+\usepackage[hyphenbreaks]{breakurl}
+\usepackage[hyphens]{url}
+
 % spanish symbols for narrative
@@
 
+%\renewcommand\topfraction{.9}
+%\renewcommand\textfraction{0.35}
+%\renewcommand\floatpagefraction{0.8}
+
 \usepackage{pgfplots}
@@
     % load the data table ...
-    \pgfplotstableread[col sep=comma]{femaleAgeDistribution.csv}{\femaleAgeDistribution}
+    \pgfplotstableread[col sep=comma]{misc/dtFemaleAgeDistribution.csv}{\femaleAgeDistribution}
         % and store the number of columns in `\NoOfCols'
@@
 
-\renewcommand{\abstractname}{Abstract} %Ajustes por traducción a español
-\begin{abstract}
-This document is a model and instructions for \LaTeX.
-This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
-or Math in Paper Title or Abstract.
-\end{abstract}
+%\renewcommand{\abstractname}{Abstract} %Ajustes por traducción a español
+%\begin{abstract}
+%
+%This document is a model and instructions for \LaTeX.
+%This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, or Math in Paper Title or Abstract.
+%\end{abstract}
 
-\renewcommand{\IEEEkeywordsname}{Palabras Clave} %Ajustes por traducción a español
-\begin{IEEEkeywords}
-aprendizaje profundo, red neuronal convolucional, rsna, procesamiento de imagenes
-\end{IEEEkeywords}
+%\renewcommand{\IEEEkeywordsname}{Palabras Clave} %Ajustes por traducción a español
+%\begin{IEEEkeywords}
+%aprendizaje profundo, red neuronal convolucional, rsna, procesamiento de imagenes
+%\end{IEEEkeywords}
+
+\section*{Abstract}
+
+\textit
+{
+La evaluación de la edad ósea esquelética es una práctica clínica comúnmente utilizada para investigar la madurez del sistema esquelético de un niño.
+Esta práctica puede ayudar a los médicos a diagnosticar afecciones que retrasan o aceleran el crecimiento y desarrollo físico.
+Recientemente, el advenimiento y la proliferación de redes neuronales convolucionales (RNC) ha mostrado ser prometedor en una variedad de aplicaciones de imágenes médicas.
+En este documento proponemos y probamos varios enfoques de aprendizaje profundo para evaluar la madurez ósea de forma automática comparando dos enfoques: por un lado, una RNC general que estima madurez ósea sobre radiografías de género masculino y femenino; por el otro, dos RNC especializadas cada una en su género respectivo.
+\textbf{Los resultados mostraron que la utilización de un/dos modelo/s general/especializado resulta más precisa para la estimación de madurez ósea.} Esta es una de las primeras evaluaciones automatizadas de la edad ósea esquelética probada en un conjunto de datos públicos donde se evalúa la utilización de una RNC general y dos RNC específicas para el género de la persona, para los cuales el código fuente está disponible, representando así una base exhaustiva para futuras investigaciones en el campo.
+}
 
 \section{Introducción}
-This document is a model and instructions for \LaTeX.
-Please observe the conference page limits.
+
+Durante el desarrollo del organismo de una persona, los huesos del esqueleto cambian de tamaño y forma, los cuales responden a una determinada edad ósea.
+Diferencia entre la edad ósea estimada de un niño y su edad cronológica podría indicar trastornos del crecimiento y anomalías endocrinas \cite{AproachToSkeletalMaturation}.
+Los médicos utilizan la evaluación de la edad ósea para estimar la madurez del sistema esquelético de un niño.
+Los métodos de evaluación de la edad ósea generalmente comienzan con tomar una sola imagen de rayos X de la mano izquierda desde la muñeca hasta las puntas de los dedos, ver Figura~\ref{fig:mano}.
+Los huesos en la imagen de rayos X se comparan con radiografías en un atlas estandarizado de desarrollo óseo.
+Tal atlas de edad ósea se basa en un gran número de radiografías recogidas de niños del mismo sexo y edad.
+
+\begin{figure}[ht!]
+  \centering
+  \includegraphics[scale=0.7]{misc/imgHuesosMano.png}
+  \caption{Huesos de una mano y muñeca humana adaptada de \cite{AtlasMedicina}}
+  \label{fig:mano}
+\end{figure}
+
+En las últimas décadas, el procedimiento de evaluación de la edad ósea se realizó de forma manual utilizando los métodos de Greulich y Pyle (GP) \cite{GP} o de Tanner-Whitehouse (TW) \cite{TW3}.
+El procedimiento GP determina la edad ósea al comparar la radiografía del paciente con un atlas de edades representativas.
+La técnica TW se basa en un sistema de puntuación que examina 20 huesos específicos.
+En ambos casos, el procedimiento de evaluación ósea requiere un tiempo considerable; a su vez, la precisión en la estimación depende de la experiencia del radiólogo y tiende a ser subjetiva.
+
+Desde 1992, preocupaciones sobre la variabilidad interobservador en la estimación manual de la edad ósea \cite{GP_variability} han llevado al establecimiento de varios métodos automáticos computarizados para la estimación de la misma.
+Los recientes avances en el aprendizaje profundo y sus aplicaciones a la visión por computadora permitieron a muchos investigadores mejorar drásticamente los resultados obtenidos con los sistemas de procesamiento de imágenes particularmente relacionados con el análisis de imágenes médicas \cite{DeepLearningInBiology}.
+A diferencia de las técnicas tradicionales de aprendizaje automático, las técnicas de aprendizaje profundo permiten que un algoritmo se programe a sí mismo aprendiendo de las imágenes dadas a un gran conjunto de datos de ejemplos etiquetados, eliminando así la necesidad de especificar reglas \cite{DeepLearning}.
+Los enfoques basados en aprendizaje profundo están ganando más atención porque en varios casos se demostró que logran e incluso superan el rendimiento a nivel humano, lo que hace que el procesamiento de imágenes de extremo a extremo sea automatizado y suficientemente rápido.
+En el campo de las imágenes médicas, las redes neuronales convolucionales (RNC) se han utilizado con éxito para el cribado de retinopatía diabética \cite{DeepLearningInDiabetics}, diagnóstico de enfermedades cardíacas \cite{DeepLearningInHeartDiseases}, detección de cáncer de pulmón \cite{DeepLearningLungCancer} y otras aplicaciones \cite{DeepLearningInBiology}.
+En el caso de la evaluación de la edad ósea, el mismo es un procedimiento que realizado manualmente requiere alrededor de 30 minutos de tiempo del médico por cada paciente.
+Cuando se realiza el mismo procedimiento utilizando un software basado en los métodos clásicos de visión por computadora, toma de 1 a 5 minutos, pero aún requiere una considerable supervisión y experiencia médica.
+Los métodos basados en aprendizaje profundo permiten evitar la ingeniería de características al aprender automáticamente la jerarquía de características discriminatorias directamente de un conjunto de ejemplos etiquetados.
+Usando un enfoque de aprendizaje profundo, el procesamiento de una imagen generalmente toma menos de 1 segundo, mientras que la precisión de estos métodos en muchos casos excede la de los métodos convencionales.
+Soluciones de redes neuronales profundas para la evaluación de la edad ósea de radiografías de mano han sido sugeridas \cite{DeepLearningAssesingSkeletalMaturity1,DeepLearningAssesingSkeletalMaturity2,DeepLearningAssesingSkeletalMaturity3}.
+Sin embargo, ninguno de estos ha evaluado en profundidad la conveniencia de separar el conjunto de datos de acuerdo al género de la radiografía y generar una RNC por cada género para investigar la precisión resultante de los mismos.
+
+En este trabajo se investiga si una RNC especializada en un determinado género podría ser más precisa en estimar la edad de una persona de acuerdo a la radiografía de su mano en lugar de una que utilice radiografías de ambos géneros.
+Nuestra contribución consiste en explorar el comportamiento de una RNC de acuerdo al conjunto de datos que es ingresado en la misma.
+Validamos la precisión de estas redes neuronales utilizando los datos de el desafío pediátrico de edad ósea 2017 organizado por la Sociedad Radiológica de América del Norte (RSNA) \cite{RSNAChallenge}.
+Este conjunto de datos ahora está disponible de manera gratuita y puede ser accedido en \cite{RSNADataSet}.
 
@@
         point meta=rawy,
+        ymin=1,
     ]
@@
 \end{itemize}
-An excellent style manual for science writers is \cite{b7}.
 
@@
 \begin{thebibliography}{00}
-\bibitem{b1} G.
-Eason, B.
-Noble, and I.
-N.
-Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
-Trans.
-Roy.
-Soc.
-London, vol.
-A247, pp.
-529--551, April 1955.
-\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-\bibitem{b6} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
-J.
-Magn.
-Japan, vol.
-2, pp.
-740--741, August 1987 [Digests 9th Annual Conf.
-Magnetics Japan, p.
-301, 1982].
-\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
+\bibitem{AproachToSkeletalMaturation} 
+Zerin JM, Hernandez RJ. 
+\textit{Approach to skeletal maturation}. 
+Hand Clin 1991; 7:53–62
+
+\bibitem{GP} 
+Greulich, W.W., Pyle, S.I.
+\textit{Radiographic atlas of skeletal development of the hand and wrist}. 
+The American Journal of the Medical Sciences 238(3), 393, 1959
+
+\bibitem{TW3} 
+Tanner JM, Healy MJ, Goldstein H, Cameron N.
+\textit{Assessment of skeletal maturity and prediction of adult height (TW3 method), 3rd ed}. 
+London, UK: Saunders Company, 2001
+
+\bibitem{GP_variability} 
+Berst MJ, Dolan L, Bogdanowicz MM, Stevens MA, Chow S, Brandser EA.
+\textit{Effect of knowledge of chronologic age on the variability of pediatric bone age determined using the Greulich and Pyle standards}. 
+AJR 2001; 176:507–510
+
+\bibitem{DeepLearningInBiology} 
+Ching, T., Himmelstein, D.S., Beaulieu-Jones, B.K., Kalinin, A.A., Do, B.T., Way, G.P., Ferrero, E., Agapow, P.M., Xie, W., Rosen, G.L., et al.
+\textit{Opportunities and obstacles for deep learning in biology and medicine}.
+bioRxiv p. 142760 (2017)
+
+\bibitem{DeepLearning} 
+LeCun Y, Bengio Y, Hinton G.
+\textit{Deep learning}.
+Nature 2015; 521:436–444
+
+\bibitem{DeepLearningInDiabetics}
+Rakhlin, A.
+\textit{Diabetic retinopathy detection through integration of deep learning classification framework}.
+bioRxiv p. 225508 (2017)
+
+\bibitem{DeepLearningInHeartDiseases}
+Korshunova, I.
+\textit{Diagnosing heart diseases with deep neural networks}.
+\\\texttt{\url{https://irakorshunova.github.io/2016/03/15/heart.html}} (2016), online; accedido 29 de Julio de 2017
+
+\bibitem{DeepLearningLungCancer}
+Daniel Hammack and Julian de Wit.
+\textit{2017 Data Science Bowl, Predicting Lung Cancer: 2nd place solution write-up}.
+\\\texttt{\url{http://blog.kaggle.com/2017/06/29/2017-data-science-bowl-predicting-lung-cancer-2nd-place-solution-write-up-daniel-hammack-and-julian-de-wit/}} (2017), online; accedido 29 de Julio de 2017
+
+\bibitem{DeepLearningAssesingSkeletalMaturity1}
+Larson, D.B., Chen, M.C., Lungren, M.P., Halabi, S.S., Stence, N.V., Langlotz, C.P.
+\textit{Performance of a deep-learning neural network model in assessing skeletal maturity on pediatric hand radiographs}.
+Radiology p. 170236 (2017)
+
+\bibitem{DeepLearningAssesingSkeletalMaturity2}
+Lee, H., Tajmir, S., Lee, J., Zissen, M., Yeshiwas, B.A., Alkasab, T.K., Choy, G., Do, S.
+\textit{Fully automated deep learning system for bone age assessment}.
+Journal of Digital Imaging pp. 1–15 (2017)
+
+\bibitem{DeepLearningAssesingSkeletalMaturity3}
+Spampinato, C., Palazzo, S., Giordano, D., Aldinucci, M., Leonardi, R.
+\textit{Deep learning for automated skeletal bone age assessment in X-ray images}.
+Medical image analysis 36, 41–51 (2017)
+
+\bibitem{RSNAChallenge}
+\textit{RSNA Pediatric Bone Age Challenge}.
+\\\texttt{\url{http://rsnachallenges.cloudapp.net/competitions/4}} (2017), online; accedido 29 de julio de 2017
+
+\bibitem{RSNADataSet}
+Stanford University Artificial Intelligence in Medicine \& Imaging
+\textit{Bone age images used in the 2017 RSNA bone age challenge competition}.
+\\\texttt{\url{https://aimi.stanford.edu/available-labeled-medical-datasets}} 
+(2017), online; accedido 29 de julio de 2017
+
+\bibitem{AtlasMedicina}
+Gilroy, A.M., MacPherson B.R., Ross L.M., Schünke M., Schulte E., Schumacher U., Voll M., Wesker K.
+\textit{Prometheus. Atlas de Anatomía}.
+pp 298, 2008
 \end{thebibliography}

### 2018-08-25 main.py
Fix using path to save model

@@ -4,6 +4,7 @@
 from keras.applications import InceptionV3, ResNet50, Xception
 from keras.layers import Flatten, Dense, Input, Dropout
 from keras.models import Model
+from keras.utils import plot_model
 from keras.optimizers import Adam, RMSprop, Adadelta, Adagrad
 from six.moves import cPickle
 import argparse
@@ -218,13 +219,6 @@ history = model.fit(
     validation_data=([img_valid, gdr_valid], [age_valid]),
     callbacks=[tbCallBack, checkpoint, reduceLROnPlat, csv_logger],
 )
-
-# Path to save model
-PATH_SAVE_MODEL = os.path.join(__location__, "model_backup", "famale_and_male")
-
-# Save weights after every epoch
-if not os.path.exists(PATH_SAVE_MODEL):
-    os.makedirs(PATH_SAVE_MODEL)
 
 # serialize model to YAML
 model_yaml = model.to_yaml()

### 2018-08-25 main_no_gender.py

@@ -170,7 +170,6 @@ history = model.fit(
     verbose=VERBOSE,
     validation_data=([img_valid], [age_valid]),
     callbacks=[tbCallBack, checkpoint, reduceLROnPlat, csv_logger],
-    #     callbacks=[tbCallBack, checkpoint],
 )
 
 

### 2018-09-10 paper/paper.tex
adding models diagrams
final paper review

@@
 \usepackage{xcolor}
+\usepackage{subcaption}
 
@@
 \renewcommand{\thesubsection}{\arabic{section}.\arabic{subsection}} 
-
+\renewcommand{\thetable}{\arabic{table}}
 %\renewcommand\topfraction{.9}
@@
         \pgfmathtruncatemacro{\NoOfCols}{\pgfplotsretval-1}
+    % load the data table ...
+    \pgfplotstableread[col sep=comma]{misc/dtMaleAgeDistribution.csv}{\maleAgeDistribution}
+        % and store the number of columns in `\NoOfCols'
+        % (minus 1 because counting in `\foreach' starts with zero
+        \pgfplotstablegetcolsof{\femaleAgeDistribution}
+        \pgfmathtruncatemacro{\NoOfCols}{\pgfplotsretval-1}
+
+%packages used for models diagrams
+\usepackage{tikz}
+\usetikzlibrary{babel}
+\usetikzlibrary{shapes.geometric}
+\usetikzlibrary{arrows.meta,arrows}
+\usepackage[T1]{fontenc}
+\usepackage{textcomp}
+\usepackage[left=2cm,right=2cm]{geometry}
+\usepackage{graphicx}
+\usepackage{amsmath}
+\usepackage{pifont}
+\usepackage{adjustbox}
 
@@
 \begin{document}
-
-\title{Título\\
+\title{Automatización de evaluación de madurez ósea a través de técnicas de aprendizaje profundo\\
 }
 
-\author{\IEEEauthorblockN{Autores}
-\IEEEauthorblockA{
-\textit{Grupo de Investigación de Aprendizaje Profundo} \\
-\textit{Departamento Ingeniería en Sistemas de Información}\\
-\textit{Universidad Tecnológica Nacional}\\
-\textit{Facultad Regional Rosario}\\
-mail@frro.utn.edu.ar} %should be hyperlink
-}
+%\author{\IEEEauthorblockN{Autores}
+%\IEEEauthorblockA{
+%\textit{Grupo de Investigación de Aprendizaje Profundo} \\
+%\textit{Departamento Ingeniería en Sistemas de Información}\\
+%\textit{Universidad Tecnológica Nacional}\\
+%\textit{Facultad Regional Rosario}\\
+%mail@frro.utn.edu.ar} %should be hyperlink
+%}
 
@@
 En este documento proponemos y probamos varios enfoques de aprendizaje profundo para evaluar la madurez ósea de forma automática comparando dos enfoques: por un lado, una RNC general que estima madurez ósea sobre radiografías de género masculino y femenino; por el otro, dos RNC especializadas cada una en su género respectivo.
-\textbf{Los resultados mostraron que la utilización de un/dos modelo/s general/especializado resulta más precisa para la estimación de madurez ósea.} Esta es una de las primeras evaluaciones automatizadas de la edad ósea esquelética probada en un conjunto de datos públicos donde se evalúa la utilización de una RNC general y dos RNC específicas para el género de la persona, para los cuales el código fuente está disponible, representando así una base exhaustiva para futuras investigaciones en el campo.
+Los resultados mostraron que la utilización de un modelo general ofrece resultados más precisos para la estimación de madurez ósea; sin embargo, los modelos especializados ofrecer resultados similares.
+Esta es una de las primeras evaluaciones automatizadas de la edad ósea esquelética probada en un conjunto de datos públicos donde se evalúa la utilización de una RNC general y dos RNC específicas para el género de la persona, para los cuales el código fuente está disponible, representando así una base exhaustiva para futuras investigaciones en el campo.
 }
@@
 
+Se realizó la comparación de dos alternativas: por un lado, un modelo general entrenado con radiografías de ambos géneros; y por otro, dos modelos entrenados cada uno con radiografías de un solo género, resultando así la obtención de un modelo específico para cada sexo: uno especializado en radiografías femeninas y otro en radiografías masculinas.
+El objetivo planteado es analizar cuál de las dos alternativas obtiene mayor precisión: dos modelos especializados en un género cada uno, donde se reduce el conjunto de datos a la mitad o un solo modelo general entrenado con radiografías de ambos géneros.
+La precisión de los modelos será definida en base al cálculo del MAE (Mean Absolute Error, Error Medio Absoluto) el cual es calculado como $\dfrac{1}{n}\sum\limits_{t=1}^{n}|e_t|$, siendo $|e_t|$ el valor absoluto de la diferencia entre cada estimación y la edad en meses etiquetada en cada observación y $n$ la cantidad de observaciones tomadas.
+
 \subsection{Conjunto de datos}
 
-The IEEEtran class file is used to format your paper and style the text. All margins, 
-column widths, line spaces, and text fonts are prescribed; please do not 
-alter them. You may note peculiarities. For example, the head margin
-measures proportionately more than is customary. This measurement 
-and others are deliberate, using specifications that anticipate your paper 
-as one part of the entire proceedings, and not as an independent document. 
-Please do not revise any of the current designations.
+El conjunto de datos utilizado ha sido extraído del desafío pediátrico de edad ósea 2017 organizado por la Sociedad Radiológica de América del Norte (RSNA) \cite{RSNAChallenge}.
+El mismo se encuentra conformado por más de 12 mil radiografías pediátricas de muñeca y mano etiquetadas por su género respectivo.
+Además, el conjunto posee una etiqueta de edad en meses estimada del paciente por un radiólogo.
+Al realizar la conversión de meses a años, las radiografías del conjunto de datos varían entre 0 y 19 años.
+Radiografías de pacientes con una maduración esquelética estimada menor a dos años han sido excluidas del experimento por dos razones.
+En primer lugar, el conjunto de datos correspondiente a esos rangos de maduración es muy pequeño (38 casos para femenino y 53 casos para masculino).
+En segundo lugar, la estimación de maduración esquelética es mayormente utilizada para casos de pubertad retrasada, pubertad precoz o baja estatura.
+Estos estudios raramente son realizados en tales rangos etarios, donde además, se evita la exposición a rayos X.
+El número total de observaciones originalmente obtenidas fue de 6,833 para hombres y 5,778 para mujeres.
+Luego de excluir aquellas de edades entre 0 y 2, ha resultado en 6,780 para hombres y 5,740 para mujeres como se muestra en la Figura~\ref{fig:distribucionEdades}.
 
 % used PGFPlots v1.14
+\begin{figure}%[htp]
 
+  \centering
+  %\mbox{
+
+  \begin{subfigure}{.5\textwidth}
+  \centering
 	\begin{tikzpicture}
-    \begin{semilogyaxis}[
+    	\begin{axis}[
         	% adjust the `width' a bit by keeping the default `height'
@@
         	xtick=data,
+        	xlabel=Años,
+        	ylabel=Número de radiografías,
         	xticklabels from table={\femaleAgeDistribution}{Anio},
@@
                 	% (because we are in a loop we have to use the "expanded" version)
-                \addlegendentryexpanded{\colname};
+                	%\addlegendentryexpanded{\colname};
         	}
-    \end{semilogyaxis}
+    	\end{axis}
+
 	\end{tikzpicture}
+  \caption{Femenino}
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+  \centering
+	\begin{tikzpicture}
+    	\begin{axis}[
+        	% adjust the `width' a bit by keeping the default `height'
+        	width=1.05*\axisdefaultwidth,
+        	height=\axisdefaultheight,
+        	% set appropriate `ymax' value so the `nodes near coords' fit to the plot
+        	% (adjusting the `ymin' value is just to make it look a little bit better)
+        	ymin=0,
+        	ymax=2000,
+        	% there should be no gap between the bars in one group
+        	ybar=0pt,
+        	% use data from the table for the xticklabels
+        	xtick=data,
+        	xlabel=Años,
+        	ylabel=Número de radiografías,
+        	xticklabels from table={\maleAgeDistribution}{Anio},
+        	% adjust the size of the bars so they don't overlap
+        	% (you can play with the numerator to change the gap between the groups)
+        	bar width=0.6/\NoOfCols,
+        	% enlarge the x limits so all of the bars are shown
+        	% (play with the value to adjust the gap on the sides of the plot)
+        	enlarge x limits={abs=0.6},
+        	% and position the legend outside of the plot to not overlap with the data
+        	%legend pos=outer north east,
+        	% add `nodes near coords'
+        	nodes near coords={
+            	% because internally PGFPlots works with floating point numbers, we
+            	% change them to fixed point numbers
+            	\pgfkeys{
+                	/pgf/fpu=true,
+                	/pgf/fpu/output format=fixed,
+            	}
+            	% truncate value count to integer
+            	\pgfmathparse{\pgfplotspointmeta}
+            	\pgfmathprintnumber{\pgfmathresult}\,
+        	},
+        	% set the style of the `nodes near coords'
+        	nodes near coords style={
+            	font=\tiny,
+            	rotate=90,
+            	anchor=west,
+        	},
+        	% as basis for the `nodes near coords' use the raw y values
+        	point meta=rawy,
+        	ymin=1,
+    	]
+        	% add the data rows for each column 
+        	\foreach \i in {1,...,\NoOfCols} {
+            	\addplot table [
+                	x expr=\coordindex,
+                	y index=\i,
+                	col sep=comma,
+            	] {\maleAgeDistribution};
+                	% to automatically add the legend entries first extract the
+                	% column name and store it in `\colname'
+                    	\pgfplotstablegetcolumnnamebyindex{\i}\of{\maleAgeDistribution}\to{\colname}
+                	% now you can add the legend entry
+                	% (because we are in a loop we have to use the "expanded" version)
+                	%\addlegendentryexpanded{\colname};
+        	}
+    	\end{axis}
+	\end{tikzpicture}
+	\caption{Masculino}
+  \end{subfigure}
+ % }
+  \caption{Distribuciones de edad ósea para radiografías de género masculino y femenino}
+  \label{fig:distribucionEdades}
+\end{figure}
 
 \subsection{Preprocesamiento}
-Define abbreviations and acronyms the first time they are used in the text, 
-even after they have been defined in the abstract. Abbreviations such as 
-IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
-abbreviations in the title or heads unless they are unavoidable.
+Un módulo de preprocesamiento ha sido desarrollado para obtener un conjunto de radiografías más homogéneo.
+El módulo se compone de tres etapas.
+En la primer etapa se realiza una nivelación de colores para resaltar en la radiografía el área ocupada por la mano.
+En la segunda etapa se detecta la mano y se recorta la imágen para que la misma ocupe la mayor cantidad de pixeles posible.
+En la tercer etapa se rota la radiografía para posicionar la mano verticalmente.
+El objetivo del módulo de preprocesamiento consiste en obtener radiografías donde la mano se posicione verticalmente y ocupe la mayor superficie posible sobre la imagen.
+Esto permite una mayor precisión en el modelo al homogeneizar el conjunto de datos.
 
-\subsection{Modelos}
-\begin{itemize}
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
-\end{itemize}
+\subsection{Sistemas Propuestos}
+El experimento para la comparación de los sistemas propuestos ha sido implementado en Python.
+La utilización y parametrización de las redes neuronales que presentan los sistemas ha sido principalmente a través de la librería Keras\footnote{Librería Keras.
+\url{https://keras.io}}.
+El código completo desarrollado para este experimento se encuentra disponible para uso académico en \url{https://github.com/deeplearningrosario/Pediatric_Bone_Age_Challenge}.
+
+Con respecto a la definición de los sistemas a utilizar para el experimento, se definieron dos arquitectuas que se describen a continuación.
+
+Se definieron dos arquitecturas para los sistemas propuestos.
+Los mismos se presentan en la Figura~\ref{fig:sistemas}.
+Los sistemas se conforman de una etapa de convolución seguida por una etapa de capas totalmente conectadas.
+En la etapa de convolución se ha utilizado ResNet-50 \cite{ResNet} con pesos pre entrenados con Imagenet \cite{Imagenet}.
+Otras redes convolucionales han sido probadas, como InceptionV3\cite{InceptionV3} y Xception\cite{Xception}, sin embargo, ResNet-50 obtuvo mejores resultados.
+La etapa de capas totalmente conectadas es la encargada de realizar la regresión de la edad basándose en los patrones extraídos por la etapa de convolución.
+La diferencia entre las dos arquitecturas para los sistemas propuestos radica en que el sistema generalizado permite utilizar el género de la radiografía como parámetro.
+El mismo es concatenado con la extracción de patrones resultantes de ResNet-50 en la etapa convolucional.
+
+Tres sistemas han sido entrenados para el experimento.
+Un sistema generalizado entrenado con radiografías de género másculino y femenino (Generalizado), y dos sistemas especializados; uno entrenado solo con radiografías de género masculino (Especializado Masculinas) y otro entrenado solo con radiografías de género femenino (Especializado Femeninas).
+Los sistemas fueron entrenados con 200 épocas, tamaño de lote de 32 y ratio de aprendizaje de 0.001.
+
+\begin{figure}
+
+  \begin{subfigure}{.5\textwidth}
+  \centering
+\begin{center}
+\begin{adjustbox}{width=\columnwidth}
+	\begin{tikzpicture}[scale = 1]	
+		\node[inner sep=0pt] (russell) at (-0.6,1.8)
+    {\includegraphics[scale=0.65]{misc/imgRadiografia.png}};
+		%FLECHA
+		\node[inner sep=0pt] (russell) at (0.55,1.95)
+    {\includegraphics[scale=0.06]{misc/imgArrowOutline.png}};
+		%PRIMER CUBO
+		\draw[thick,-](1.5,1,1)--(1.5,3,1);
+		\draw[thick,-](1.5,3,1)--(1.75,3,1);
+		\draw[thick,-](1.75,3,1)--(1.75,1,1);
+		\draw[thick,-](1.75,1,1)--(1.5,1,1);
+		\draw[thick,-](1.5,3,1)--(1.5,3,-1);		
+		\draw[thick,-](1.5,3,-1)--(1.75,3,-1);
+		\draw[thick,-](1.75,3,-1)--(1.75,3,1);
+		\draw[thick,-](1.75,3,-1)--(1.75,1,-1);
+		\draw[thick,-](1.75,1,-1)--(1.75,1,1);
+		%SEGUNDO RECTANGULO
+		\draw[thick,-](4,1.5,1)--(4,2.5,1);
+		\draw[thick,-](4,2.5,1)--(4,2.5,0);
+		\draw[thick,-](4,2.5,0)--(4,1.5,0);
+		\draw[thick,-](4,1.5,0)--(4,1.5,1);
+		%UNIONES ENTRE 1° Y 2° FIGURA
+		\draw[thick,dashed,-](1.75,3,1)--(4,2.5,1);
+		\draw[thick,dashed,-](1.75,1,1)--(4,1.5,1);
+		\draw[thick,dashed,-](1.75,3,-1)--(4,2.5,0);
+		\draw[thick,dashed,-](1.75,1,-1)--(4,1.5,0);
+		%FLECHA
+		\draw[thick,->](4.6,2.3,1)--(5.75,2.3,1);
+		%TERCER RECTANGULO 
+		\draw[thick,-](6,1.25,1)--(6,3.25,1);
+		\draw[thick,-](6,3.25,1)--(6.25,3.25,1);
+		\draw[thick,-](6.25,3.25,1)--(6.25,1.25,1);
+		\draw[thick,-](6.25,1.25,1)--(6,1.25,1);
+		%FLECHA
+		\draw[thick,->](6.35,2.3,1)--(7.9,2.3,1);
+		%CUARTO RECTANGULO 
+		\draw[thick,-](8,1.25,1)--(8,3.25,1);
+		\draw[thick,-](8,3.25,1)--(8.25,3.25,1);
+		\draw[thick,-](8.25,3.25,1)--(8.25,1.25,1);
+		\draw[thick,-](8.25,1.25,1)--(8,1.25,1);
+		%FLECHA
+		\draw[thick,->](8.35,2.3,1)--(9.125,2.3,1);
+		%QUINTO RECTANGULO 
+		\draw[thick,-](9.225,1.25,1)--(9.225,3.25,1);
+		\draw[thick,-](9.225,3.25,1)--(9.475,3.25,1);
+		\draw[thick,-](9.475,3.25,1)--(9.475,1.25,1);
+		\draw[thick,-](9.475,1.25,1)--(9.225,1.25,1);
+		%FLECHA
+		\draw[thick,->](9.575,2.3,1)--(10.25,2.3,1);
+		%SEXTO RECTANGULO 
+		\draw[thick,-](10.35,1.25,1)--(10.35,3.25,1);
+		\draw[thick,-](10.35,3.25,1)--(10.60,3.25,1);
+		\draw[thick,-](10.60,3.25,1)--(10.60,1.25,1);
+		\draw[thick,-](10.60,1.25,1)--(10.35,1.25,1);
+		%FLECHA
+		\draw[thick,->](10.7,2.3,1)--(11.375,2.3,1);
+		%SEPTIMO RECTANGULO 
+		\draw[thick,-](11.475,1.25,1)--(11.475,3.25,1);
+		\draw[thick,-](11.475,3.25,1)--(11.725,3.25,1);
+		\draw[thick,-](11.725,3.25,1)--(11.725,1.25,1);
+		\draw[thick,-](11.725,1.25,1)--(11.475,1.25,1);
+		%FLECHA
+		\draw[thick,->](11.825,2.3,1)--(12.5,2.3,1);
+		%OCTAVO RECTANGULO 
+		\draw[thick,-](12.6,1.5,1)--(12.6,3,1);
+		\draw[thick,-](12.6,3,1)--(12.85,3,1);
+		\draw[thick,-](12.85,3,1)--(12.85,1.5,1);
+		\draw[thick,-](12.85,1.5,1)--(12.6,1.5,1);
+		%FLECHA
+		\draw[thick,->](12.95,2.3,1)--(13.625,2.3,1);
+		%NOVENO RECTANGULO 
+		\draw[thick,-](13.725,1.5,1)--(13.725,3,1);
+		\draw[thick,-](13.725,3,1)--(13.975,3,1);
+		\draw[thick,-](13.975,3,1)--(13.975,1.5,1);
+		\draw[thick,-](13.975,1.5,1)--(13.725,1.5,1);
+		%FLECHA
+		%\draw[thick,->](14.075,2.3,1)--(14.9,2.3,1);
+		%DECIMO RECTANGULO 
+		%\draw[thick,-](15,1.7,1)--(15,2.8,1);
+		%\draw[thick,-](15,2.8,1)--(15.25,2.8,1);
+		%\draw[thick,-](15.25,2.8,1)--(15.25,1.7,1);
+		%\draw[thick,-](15.25,1.7,1)--(15,1.7,1);
+		%FLECHA HACERLA DOBLE
+		\node[inner sep=0pt] (russell) at (13.975,1.88)
+    {\includegraphics[scale=0.04]{misc/imgArrowOutline.png}};
+		%ONCEAVO RECTANGULO 
+		\draw[thick,-](15,1.9,1)--(15,2.6,1);
+		\draw[thick,-](15,2.6,1)--(17,2.6,1);
+		\draw[thick,-](17,2.6,1)--(17,1.9,1);
+		\draw[thick,-](17,1.9,1)--(15,1.9,1);
+		%TEXTOS
+		\node[scale=0.65] at (15.65,1.98) {Y};
+		\node[scale=0.65] at (15.65,1.7) {edad ósea estimada};
+		\node[scale=1] at (5.75,0.68) {\ding{115}};
+		\node[scale=0.75] at (5.7,0.35) {salida rn50 1000};
+		\node[scale=1] at (7.75,0.68) {\ding{115}};
+		\node[scale=0.75] at (7.8,0.35) {densa 1000 relu};
+		\node[scale=1] at (8.95,3.1) {\ding{116}};
+		\node[scale=0.75] at (8.95,3.4) {dropout 0.2};
+		\node[scale=1] at (10.1,0.68) {\ding{115}};
+		\node[scale=0.75] at (10.1,0.35) {densa 1000 relu};
+		\node[scale=1] at (11.22,3.1) {\ding{116}};
+		\node[scale=0.75] at (11.25,3.4) {dropout 0.2};
+		\node[scale=1] at (12.35,0.9) {\ding{115}};
+		\node[scale=0.75] at (12.4,0.6) {densa 240 relu};
+		\node[scale=1] at (13.457,2.8) {\ding{116}};
+		\node[scale=0.75] at (13.4,3.1) {densa 1 relu};
+		%\node[scale=1] at (14.75,1.1) {\ding{115}};
+		%\node[scale=0.75] at (14.9,0.8) {densa 1 regresión};
+		\node[scale=1] at (4.2,3.2) {ResNet-50};
+		\node[scale=1.4] at (3.5,4.5) {Convolución};
+		\node[scale=1.4] at (10,4.5) {Capas totalmente conectadas};
+		\node[inner sep=0pt] (russell) at (3.35,3.75)
+    {\includegraphics[width=4.5cm,height=0.25cm]{misc/imgLlave.png}};
+		\node[inner sep=0pt] (russell) at (10,3.75)
+    {\includegraphics[width=9cm,height=0.25cm]{misc/imgLlave.png}};
+	\end{tikzpicture}
+\end{adjustbox}
+\end{center}
+ \caption{Sistema propuesto especializado en género}
+  \end{subfigure}%
+\\
+\\
+\\
+\begin{subfigure}{.5\textwidth}
+  \centering
+\begin{center}
+\begin{adjustbox}{width=\columnwidth}
+	\begin{tikzpicture}[scale = 1]	
+		\node[inner sep=0pt] (russell) at (-0.6,3.05)
+    {\includegraphics[scale=0.65]{misc/imgRadiografia.png}};
+		%FLECHA
+		\node[inner sep=0pt] (russell) at (0.55,3.2)
+    {\includegraphics[scale=0.06]{misc/imgArrowOutline.png}};
+		%PRIMER CUBO
+		\draw[thick,-](1.5,2.25,1)--(1.5,4.25,1);
+		\draw[thick,-](1.5,4.25,1)--(1.75,4.25,1);
+		\draw[thick,-](1.75,4.25,1)--(1.75,2.25,1);
+		\draw[thick,-](1.75,2.25,1)--(1.5,2.25,1);
+		\draw[thick,-](1.5,4.25,1)--(1.5,4.25,-1);		
+		\draw[thick,-](1.5,4.25,-1)--(1.75,4.25,-1);
+		\draw[thick,-](1.75,4.25,-1)--(1.75,4.25,1);
+		\draw[thick,-](1.75,4.25,-1)--(1.75,2.25,-1);
+		\draw[thick,-](1.75,2.25,-1)--(1.75,2.25,1);
+		%SEGUNDO RECTANGULO
+		\draw[thick,-](4,2.75,1)--(4,3.75,1);
+		\draw[thick,-](4,3.75,1)--(4,3.75,0);
+		\draw[thick,-](4,3.75,0)--(4,2.75,0);
+		\draw[thick,-](4,2.75,0)--(4,2.75,1);
+		%UNIONES ENTRE 1° Y 2° FIGURA
+		\draw[thick,dashed,-](1.75,4.25,1)--(4,3.75,1);
+		\draw[thick,dashed,-](1.75,2.25,1)--(4,2.75,1);
+		\draw[thick,dashed,-](1.75,4.25,-1)--(4,3.75,0);
+		\draw[thick,dashed,-](1.75,2.25,-1)--(4,2.75,0);
+		%FLECHA
+		\draw[thick,->](4.6,3.55,1)--(5.75,3.55,1);
+		%TERCER RECTANGULO 
+		\draw[thick,-](6,2.5,1)--(6,4.5,1);
+		\draw[thick,-](6,4.5,1)--(6.25,4.5,1);
+		\draw[thick,-](6.25,4.5,1)--(6.25,2.5,1);
+		\draw[thick,-](6.25,2.5,1)--(6,2.5,1);
+		%FLECHA
+		\draw[thick,->](6.35,3.55,1)--(7.6,2.3,1);
+		%CUADRADO inferior
+		\draw[thick,-](2.55,-0.75,1)--(2.55,1.25,1);
+		\draw[thick,-](2.55,1.25,1)--(4.55,1.25,1);
+		\draw[thick,-](4.55,1.25,1)--(4.55,-0.75,1);
+		\draw[thick,-](4.55,-0.75,1)--(2.55,-0.75,1);
+		%FLECHA inferior
+		\node[inner sep=0pt] (russell) at (4.85,-0.1)
+    {\includegraphics[scale=0.06]{misc/imgArrowOutline.png}};
+		%RECTANGULO inferior
+		\draw[thick,-](5.85,-0.25,1)--(5.85,0.75,1);
+		\draw[thick,-](5.85,0.75,1)--(6.1,0.75,1);
+		\draw[thick,-](6.1,0.755,1)--(6.1,-0.25,1);
+		\draw[thick,-](6.1,-0.25,1)--(5.85,-0.25,1);
+		%FLECHA diagonal desde inferior a superior
+		\draw[thick,->](6.2,0.25,1)--(7.6,2.1,1);
+		%CUARTO RECTANGULO 
+		\draw[thick,-](7.7,1.25,1)--(7.7,3.25,1);
+		\draw[thick,-](7.7,3.25,1)--(7.95,3.25,1);
+		\draw[thick,-](7.95,3.25,1)--(7.95,1.25,1);
+		\draw[thick,-](7.95,1.25,1)--(7.7,1.25,1);
+		%FLECHA
+		\draw[thick,->](8.05,2.3,1)--(8.65,2.3,1);
+		%QUINTO RECTANGULO 
+		\draw[thick,-](8.75,1.25,1)--(8.75,3.25,1);
+		\draw[thick,-](8.75,3.25,1)--(9,3.25,1);
+		\draw[thick,-](9,3.25,1)--(9,1.25,1);
+		\draw[thick,-](9,1.25,1)--(8.75,1.25,1);
+		%FLECHA
+		\draw[thick,->](9.1,2.3,1)--(9.7,2.3,1);
+		%SEXTO RECTANGULO 
+		\draw[thick,-](9.8,1.25,1)--(9.8,3.25,1);
+		\draw[thick,-](9.8,3.25,1)--(10.05,3.25,1);
+		\draw[thick,-](10.05,3.25,1)--(10.05,1.25,1);
+		\draw[thick,-](10.05,1.25,1)--(9.8,1.25,1);
+		%FLECHA
+		\draw[thick,->](10.15,2.3,1)--(10.75,2.3,1);
+		%SEXTO RECTANGULO 
+		\draw[thick,-](10.85,1.25,1)--(10.85,3.25,1);
+		\draw[thick,-](10.85,3.25,1)--(11.1,3.25,1);
+		\draw[thick,-](11.1,3.25,1)--(11.1,1.25,1);
+		\draw[thick,-](11.1,1.25,1)--(10.85,1.25,1);
+		%FLECHA
+		\draw[thick,->](11.2,2.3,1)--(11.8,2.3,1);
+		%SEPTIMO RECTANGULO 
+		\draw[thick,-](11.9,1.25,1)--(11.9,3.25,1);
+		\draw[thick,-](11.9,3.25,1)--(12.15,3.25,1);
+		\draw[thick,-](12.15,3.25,1)--(12.15,1.25,1);
+		\draw[thick,-](12.15,1.25,1)--(11.9,1.25,1);
+		%FLECHA
+		\draw[thick,->](12.25,2.3,1)--(12.85,2.3,1);
+		%OCTAVO RECTANGULO 
+		\draw[thick,-](12.95,1.5,1)--(12.95,3,1);
+		\draw[thick,-](12.95,3,1)--(13.2,3,1);
+		\draw[thick,-](13.2,3,1)--(13.2,1.5,1);
+		\draw[thick,-](13.2,1.5,1)--(12.95,1.5,1);
+		%FLECHA
+		\draw[thick,->](13.30,2.3,1)--(13.85,2.3,1);
+		%NOVENO RECTANGULO 
+		\draw[thick,-](14,1.5,1)--(14,3,1);
+		\draw[thick,-](14,3,1)--(14.25,3,1);
+		\draw[thick,-](14.25,3,1)--(14.25,1.5,1);
+		\draw[thick,-](14.25,1.5,1)--(14,1.5,1);
+		%FLECHA
+		%\draw[thick,->](14.35,2.3,1)--(14.9,2.3,1);
+		%DECIMO RECTANGULO 
+		%\draw[thick,-](15,1.7,1)--(15,2.8,1);
+		%\draw[thick,-](15,2.8,1)--(15.25,2.8,1);
+		%\draw[thick,-](15.25,2.8,1)--(15.25,1.7,1);
+		%\draw[thick,-](15.25,1.7,1)--(15,1.7,1);
+		%FLECHA HACERLA DOBLE
+		\node[inner sep=0pt] (russell) at (14.27,1.88)
+    {\includegraphics[scale=0.04]{misc/imgArrowOutline.png}};
+		%ONCEAVO RECTANGULO 
+		\draw[thick,-](15,1.9,1)--(15,2.6,1);
+		\draw[thick,-](15,2.6,1)--(17,2.6,1);
+		\draw[thick,-](17,2.6,1)--(17,1.9,1);
+		\draw[thick,-](17,1.9,1)--(15,1.9,1);
+		%TEXTOS
+		\node[scale=0.65] at (15.6,1.98) {Y};
+		\node[scale=0.65] at (15.6,1.7) {edad ósea estimada};
+		\node[scale=1.4] at (3.2,0.25) {Género};
+		\node[scale=1.4] at (3.2,-0.5) {M/F};
+		\node[scale=1] at (5.6,-0.85) {\ding{115}};
+		\node[scale=0.75] at (5.6,-1.15) {densa 32 relu};
+		\node[scale=1] at (5.75,1.93) {\ding{115}};
+		\node[scale=0.75] at (5.5,1.6) {salida rn50 1000};
+		\node[scale=1] at (7.43,3.1) {\ding{116}};
+		\node[scale=0.75] at (7.55,3.4) {concat 1032};
+		\node[scale=1] at (8.5,0.68) {\ding{115}};
+		\node[scale=0.75] at (8.5,0.35) {densa 1000 relu};
+		\node[scale=1] at (9.53,3.1) {\ding{116}};
+		\node[scale=0.75] at (9.53,3.4) {dropout 0.2};
+		\node[scale=1] at (10.6,0.68) {\ding{115}};
+		\node[scale=0.75] at (10.6,0.35) {densa 1000 relu};
+		\node[scale=1] at (11.63,3.1) {\ding{116}};
+		\node[scale=0.75] at (11.63,3.4) {dropout 0.2};
+		\node[scale=1] at (12.7,0.9) {\ding{115}};
+		\node[scale=0.75] at (12.7,0.6) {densa 240 relu};
+		\node[scale=1] at (13.73,2.8) {\ding{116}};
+		\node[scale=0.75] at (13.73,3.1) {densa 1 relu};
+		%\node[scale=1] at (14.75,1.1) {\ding{115}};
+		%\node[scale=0.75] at (14.9,0.8) {densa 1 regresión};
+		\node[scale=1] at (4.2,4.45) {ResNet-50};
+		\node[scale=1.4] at (3.5,5.75) {Convolución};
+		\node[scale=1.4] at (10,5.75) {Capas totalmente conectadas};
+		\node[inner sep=0pt] (russell) at (3.35,5)
+    {\includegraphics[width=4.5cm,height=0.25cm]{misc/imgLlave.png}};
+		\node[inner sep=0pt] (russell) at (10,5)
+    {\includegraphics[width=8.5cm,height=0.25cm]{misc/imgLlave.png}};
+	\end{tikzpicture}
+\end{adjustbox}
+\end{center}
+ \caption{Sistema propuesto generalizado para ambos géneros}
+  \end{subfigure}
+   \caption{Sistemas propuestos}
+   \label{fig:sistemas}
+\end{figure}
 
 \section{Resultados del experimento}
-Number equations consecutively. To make your 
-equations more compact, you may use the solidus (~/~), the exp function, or 
-appropriate exponents. Italicize Roman symbols for quantities and variables, 
-but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-sign. Punctuate equations with commas or periods when they are part of a 
-sentence, as in:
-\begin{equation}
-a+b=\gamma\label{eq}
-\end{equation}
-
-Be sure that the 
-symbols in your equation have been defined before or immediately following 
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
+Para los experimentos realizados se ha calculado el MAE resultante en cada uno de los sistemas propuestos con un conjunto de datos de radiografías masculinas y/o femeninas según corresponda.
+Los resultados se muestran en el Cuadro~\ref{table:tablaResultados}.
+En cada fila se muestran los MAE en meses resultantes para cada sistema.
+La primer columna especifica el sistema utilizado.
+Segunda columna el MAE resultante para el conjunto de radiografías femeninas.
+Tercer columna el MAE resultante para el conjunto de radiografías masculinas.
+Puede observarse que el sistema generalizado obtiene mejores resultados para ambos conjuntos de datos.
+El sistema generalizado presenta mayor precisión con respecto al sistema especializado en radiografías femeninas en \textasciitilde{}1.066 meses.
+También presenta mayor presición con respecto al sistema especializado en radiografías masculinas en \textasciitilde{}0.571 meses.
+\begin{table}[]
+\centering
+\resizebox{.48\textwidth}{!}{%
+\begin{tabular}{l|>{\centering\arraybackslash}p{1in}>{\centering\arraybackslash}m{1in}ll}
+ 							&Femeninas	&Masculinas \\ \hline
+ Generalizado				&9.326	&9.120	\\ \hline
+ Especializado Femeninas	&10.392	&-  		\\ \hline
+ Especializado Masculinas	&-			&9.691 
+\end{tabular}
+}
+\caption{MAE en meses de los sistemas de acuerdo al género de radiografía utilizado}
+\label{table:tablaResultados}
+\end{table}
 
@@
 
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
-
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
-
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
-
-{\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
-
-{\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
-
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
-
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
+En esta sección se presentan conclusiones sobre la experimentación realizada y pasos a seguir para aumentar la precisión de los sistemas tratados.
 
 \subsection{Conclusiones}
-\begin{itemize}
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-\end{itemize}
+Nuestra motivación en esta experimentación fue evaluar los diferentes comportamientos que puede presentar una red neuronal de acuerdo a variaciones en el conjunto de datos de entrada como así también los parámetros utilizados en la misma.
+Se han presentado los resultados obtenidos sobre los sistemas propuestos.
+Se ha observado que un sistema que acepte ambos géneros ha obtenido mayor precisión.
+Sin embargo, la pequeña diferencia en precisión observada al compararlo con los sistemas especializados da lugar a pensar mejoras que podrían disminuir tal diferencia.
+Además, se han desarrollado arquitecturas para la extracción de patrones y estimación de edad de una radiografía de mano y muñeca pediátrica que podría ser de gran utilidad para aquellas personas interesadas en abordar problemáticas similares, como así también en el ámbito de la medicina a través de su implementación en instituciones de salud, como Hospitales o Sanatorios, para asistir en la labor de pediátras, endocrinólogos, radiólogos y/u otros especialistas.
 
 \subsection{Trabajo Futuro}
-\textbf{The class file is designed for, but not limited to, six authors.} A 
-minimum of one author is required for all conference articles. Author names 
-should be listed starting from left to right and then moving down to the 
-next line. This is the author sequence that will be used in future citations 
-and by indexing services. Names should not be listed in columns nor group by 
-affiliation. Please keep your affiliations as succinct as possible (for 
-example, do not differentiate among departments of the same organization).
+En una segunda fase de experimentación el desafío se centra en aumentar la precisión de los sistemas.
+El módulo de preprocesamiento actual ha probado su utilidad aumentando la precisión de los modelos en 0,2 meses.
+En una segunda fase se reemplazará el módulo por una red neuronal que realice las mismas funciones con mayor precisión, lo que se estima que disminuirá el error de los modelos.
+Además, se continuará experimentando variaciones estructurales en el etapa de capas totalmente conectadas, como así también variaciones en la etapa convolucional.
+En cuanto al conjunto de datos, se aplicarán técnicas de aumento de datos (data augmentation) para incrementar la cantidad de radiografías con las que sería posible entrenar los sistemas.
 
@@
 \bibitem{AproachToSkeletalMaturation} 
-Zerin JM, Hernandez RJ. 
+Zerin, J. M., \& Hernandez, R. J. (1991). 
 \textit{Approach to skeletal maturation}. 
-Hand Clin 1991; 7:53–62
+Hand clinics, 7(1), 53-62.
 
 \bibitem{GP} 
-Greulich, W.W., Pyle, S.I.
+Greulich, W. W., Pyle, S. I., \& Todd, T. W. (1959).
 \textit{Radiographic atlas of skeletal development of the hand and wrist}. 
-The American Journal of the Medical Sciences 238(3), 393, 1959
+(Vol. 2, pp. 150-159). Stanford: Stanford university press.
 
 \bibitem{TW3} 
-Tanner JM, Healy MJ, Goldstein H, Cameron N.
-\textit{Assessment of skeletal maturity and prediction of adult height (TW3 method), 3rd ed}. 
-London, UK: Saunders Company, 2001
+Tanner, J. M., Healy, M. R. J., Goldstein, H., \& Cameron, N. (2001).
+\textit{Assessment of skeletal maturity and prediction of adult height (TW3 method)}. 
+WB Saunders, London, 243-254.
 
 \bibitem{GP_variability} 
-Berst MJ, Dolan L, Bogdanowicz MM, Stevens MA, Chow S, Brandser EA.
+Berst, M. J., Dolan, L., Bogdanowicz, M. M., Stevens, M. A., Chow, S., \& Brandser, E. A. (2001).
 \textit{Effect of knowledge of chronologic age on the variability of pediatric bone age determined using the Greulich and Pyle standards}. 
-AJR 2001; 176:507–510
+American Journal of Roentgenology, 176(2), 507-510.
 
 \bibitem{DeepLearningInBiology} 
-Ching, T., Himmelstein, D.S., Beaulieu-Jones, B.K., Kalinin, A.A., Do, B.T., Way, G.P., Ferrero, E., Agapow, P.M., Xie, W., Rosen, G.L., et al.
+Ching, T., Himmelstein, D. S., Beaulieu-Jones, B. K., Kalinin, A. A., Do, B. T., Way, G. P., ... \& Xie, W. (2018).
 \textit{Opportunities and obstacles for deep learning in biology and medicine}.
-bioRxiv p. 142760 (2017)
+Journal of The Royal Society Interface, 15(141), 20170387.
 
 \bibitem{DeepLearning} 
-LeCun Y, Bengio Y, Hinton G.
+LeCun, Y., Bengio, Y., \& Hinton, G. (2015).
 \textit{Deep learning}.
-Nature 2015; 521:436–444
+Nature, 521(7553), 436.
 
 \bibitem{DeepLearningInDiabetics}
-Rakhlin, A.
-\textit{Diabetic retinopathy detection through integration of deep learning classification framework}.
-bioRxiv p. 225508 (2017)
+Rakhlin, A. (2018).
+\textit{Diabetic Retinopathy detection through integration of Deep Learning classification framework}.
+bioRxiv, 225508.
 
 \bibitem{DeepLearningInHeartDiseases}
-Korshunova, I.
+Korshunova, I. (2017).
 \textit{Diagnosing heart diseases with deep neural networks}.
-\\\texttt{\url{https://irakorshunova.github.io/2016/03/15/heart.html}} (2016), online; accedido 29 de Julio de 2017
+\\\texttt{\url{https://irakorshunova.github.io/2016/03/15/heart.html}}, accedido 29 de Julio de 2017.
 
 \bibitem{DeepLearningLungCancer}
-Daniel Hammack and Julian de Wit.
+Daniel Hammack and Julian de Wit. (2017)
 \textit{2017 Data Science Bowl, Predicting Lung Cancer: 2nd place solution write-up}.
-\\\texttt{\url{http://blog.kaggle.com/2017/06/29/2017-data-science-bowl-predicting-lung-cancer-2nd-place-solution-write-up-daniel-hammack-and-julian-de-wit/}} (2017), online; accedido 29 de Julio de 2017
+\\\texttt{\url{http://blog.kaggle.com/2017/06/29/2017-data-science-bowl-predicting-lung-cancer-2nd-place-solution-write-up-daniel-hammack-and-julian-de-wit/}}, accedido 29 de Julio de 2017.
 
 \bibitem{DeepLearningAssesingSkeletalMaturity1}
-Larson, D.B., Chen, M.C., Lungren, M.P., Halabi, S.S., Stence, N.V., Langlotz, C.P.
+Larson, D. B., Chen, M. C., Lungren, M. P., Halabi, S. S., Stence, N. V., \& Langlotz, C. P. (2017).
 \textit{Performance of a deep-learning neural network model in assessing skeletal maturity on pediatric hand radiographs}.
-Radiology p. 170236 (2017)
+Radiology, 287(1), 313-322.
 
 \bibitem{DeepLearningAssesingSkeletalMaturity2}
-Lee, H., Tajmir, S., Lee, J., Zissen, M., Yeshiwas, B.A., Alkasab, T.K., Choy, G., Do, S.
+Lee, H., Tajmir, S., Lee, J., Zissen, M., Yeshiwas, B. A., Alkasab, T. K., ... \& Do, S. (2017).
 \textit{Fully automated deep learning system for bone age assessment}.
-Journal of Digital Imaging pp. 1–15 (2017)
+Journal of digital imaging, 30(4), 427-441.
 
 \bibitem{DeepLearningAssesingSkeletalMaturity3}
-Spampinato, C., Palazzo, S., Giordano, D., Aldinucci, M., Leonardi, R.
+Spampinato, C., Palazzo, S., Giordano, D., Aldinucci, M., \& Leonardi, R. (2017).
 \textit{Deep learning for automated skeletal bone age assessment in X-ray images}.
-Medical image analysis 36, 41–51 (2017)
+Medical image analysis, 36, 41-51.
 
@@
 \textit{RSNA Pediatric Bone Age Challenge}.
-\\\texttt{\url{http://rsnachallenges.cloudapp.net/competitions/4}} (2017), online; accedido 29 de julio de 2017
+\\\texttt{\url{http://rsnachallenges.cloudapp.net/competitions/4}}, accedido 29 de julio de 2017.
 
 \bibitem{RSNADataSet}
-Stanford University Artificial Intelligence in Medicine \& Imaging
+Stanford University Artificial Intelligence in Medicine \& Imaging (2017).
 \textit{Bone age images used in the 2017 RSNA bone age challenge competition}.
-\\\texttt{\url{https://aimi.stanford.edu/available-labeled-medical-datasets}} 
-(2017), online; accedido 29 de julio de 2017
+\\\texttt{\url{https://aimi.stanford.edu/available-labeled-medical-datasets}}, accedido 29 de julio de 2017.
 
 \bibitem{AtlasMedicina}
-Gilroy, A.M., MacPherson B.R., Ross L.M., Schünke M., Schulte E., Schumacher U., Voll M., Wesker K.
+Gilroy, A.M., MacPherson B.R., Ross L.M., Schünke M., Schulte E., Schumacher U., Voll M., \& Wesker K. (2008).
 \textit{Prometheus. Atlas de Anatomía}.
-pp 298, 2008
+pp 298.
+
+\bibitem{ResNet}
+He, K., Zhang, X., Ren, S., \& Sun, J. (2016). 
+\textit{Deep residual learning for image recognition}.
+In Proceedings of the IEEE conference on computer vision and pattern recognition (pp. 770-778).
+
+\bibitem{Imagenet}
+Deng, J., Dong, W., Socher, R., Li, L. J., Li, K., \& Fei-Fei, L. (2009, June). 
+\textit{Imagenet: A large-scale hierarchical image database}. In Computer Vision and Pattern Recognition, 2009. CVPR 2009. IEEE Conference on (pp. 248-255). Ieee.
+
+\bibitem{InceptionV3}
+Szegedy, C., Vanhoucke, V., Ioffe, S., Shlens, J., \& Wojna, Z. (2016). 
+\textit{Rethinking the inception architecture for computer vision}. In Proceedings of the IEEE conference on computer vision and pattern recognition (pp. 2818-2826).
+
+\bibitem{Xception}
+Chollet, F. (2017).
+\textit{Xception: Deep learning with depthwise separable convolutions}. arXiv preprint, 1610-02357.
 \end{thebibliography}

### 2018-09-11 main.py
Add training monitor

@@ -1,6 +1,7 @@
 #!/usr/bin/python3
 # ./main.py --load_weight ./weight_file.h5
 
+from trainingmonitor import TrainingMonitor
 from keras.applications import InceptionV3, ResNet50, Xception
 from keras.layers import Flatten, Dense, Input, Dropout
 from keras.models import Model
@@ -40,7 +41,9 @@ CNN = "RN50"
 def readFile(gender, dataset, X_img=None, x_gender=None, y_age=None):
     print("Reading", gender, dataset, "data...")
     file_name = gender + "-" + dataset + "-" + ".hdf5"
-    with h5py.File(os.path.join(__location__, "packaging-dataset", file_name), "r+") as f:
+    with h5py.File(
+        os.path.join(__location__, "packaging-dataset", file_name), "r+"
+    ) as f:
         f_img = f["img"][()]
         f_gender = f["gender"][()]
         f_age = f["age"][()]
@@ -83,11 +86,7 @@ img_test, gdr_test, age_test = readFile(
 
 
 def randomDataSet(X_img, x_gender, y_age):
-    random_id = np.random.choice(
-        X_img.shape[0],
-        size=X_img.shape[0],
-        replace=False
-    )
+    random_id = np.random.choice(X_img.shape[0], size=X_img.shape[0], replace=False)
     X_img = X_img[random_id]
     x_gender = x_gender[random_id]
     y_age = y_age[random_id]
@@ -210,6 +209,23 @@ if not os.path.exists(PATH_SAVE_MODEL):
 
 csv_logger = keras.callbacks.CSVLogger(os.path.join(PATH_SAVE_MODEL, "training.csv"))
 
+# Save model fit progress
+PATH_TRAING_MONITOR = os.path.join(PATH_SAVE_MODEL, "training_monitor")
+if not os.path.exists(PATH_TRAING_MONITOR):
+    os.makedirs(PATH_TRAING_MONITOR)
+
+figPath = os.path.sep.join([PATH_TRAING_MONITOR, "{}.png".format(os.getpid())])
+jsonPath = os.path.sep.join([PATH_TRAING_MONITOR, "{}.json".format(os.getpid())])
+
+callbacks = [
+    TrainingMonitor(figPath, jsonPath=jsonPath),
+    # tbCallBack,
+    # checkpoint,
+    reduceLROnPlat,
+    csv_logger,
+]
+
+
 history = model.fit(
     [img_train, gdr_train],
[…]

### 2018-09-11 trainingmonitor.py

@@ -1,0 +1,64 @@
+# import the necessary packages
+from keras.callbacks import BaseLogger
+import matplotlib.pyplot as plt
+import numpy as np
+import json
+import os
+
+
+class TrainingMonitor(BaseLogger):
+
+    def __init__(self, figPath, jsonPath=None, startAt=0):
+        # store the output path for the figure, the path to the JSON
+        # serialized file, and the starting epoch
+        super(TrainingMonitor, self).__init__()
+        self.figPath = figPath
+        self.jsonPath = jsonPath
+        self.startAt = startAt
+
+    def on_train_begin(self, logs={}):
+        # initialize the history dictionary
+        self.H = {}
+        # if the JSON history path exists, load the training history
+        if self.jsonPath is not None:
+            if os.path.exists(self.jsonPath):
+                self.H = json.loads(open(self.jsonPath).read())
+                # check to see if a starting epoch was supplied
+                if self.startAt > 0:
+                    # loop over the entries in the history log and
+                    # trim any entries that are past the starting
+                    # epoch
+                    for k in self.H.keys():
+                        self.H[k] = self.H[k][:self.startAt]
+
+    def on_epoch_end(self, epoch, logs={}):
+        # loop over the logs and update the loss, accuracy, etc.
+        # for the entire training process
+        for (k, v) in logs.items():
+            l = self.H.get(k, [])
+            l.append(v)
+            self.H[k] = l
+        # check to see if the training history should be serialized
+        # to file
+        if self.jsonPath is not None:
+            f = open(self.jsonPath, "w")
+            f.write(json.dumps(self.H))
+            f.close()
+        # ensure at least two epochs have passed before plotting
+        # (epoch starts at zero)
+        if len(self.H["loss"]) > 1:
+            # plot the training loss and accuracy
+            N = np.arange(0, len(self.H["loss"]))
+            plt.style.use("ggplot")
+            plt.figure()
+            plt.plot(N, self.H["loss"], label="train_loss")
+            plt.plot(N, self.H["val_loss"], label="val_loss")
+            plt.plot(N, self.H["acc"], label="train_acc")
+            plt.plot(N, self.H["val_acc"], label="val_acc")
+            plt.title("Training Loss and Accuracy [Epoch {}]".format(len(self.H["loss"])))
+            plt.xlabel("Epoch #")
+            plt.ylabel("Loss/Accuracy")
+            plt.legend()
+            # save the figure
+            plt.savefig(self.figPath)
+            plt.close()

### 2018-09-11 main.py
Save loss and mean during training, epoch by epoch

@@ -23,7 +23,7 @@ args = vars(ap.parse_args())
 __location__ = os.path.realpath(os.path.join(os.getcwd(), os.path.dirname(__file__)))
 
 # network and training
-EPOCHS = 100
+EPOCHS = 50
 BATCH_SIZE = 32
 VERBOSE = 1
 # https://keras.io/optimizers
@@ -33,9 +33,9 @@ OPTIMIZER = Adam(lr=0.001, amsgrad=True)
 # OPTIMIZER = Adagrad(lr=0.05)
 
 # Image processing layer
-# CNN = 'Xception'
+CNN = "Xception"
 # CNN = 'IV3'
-CNN = "RN50"
+# CNN = "RN50"
 
 
 def readFile(gender, dataset, X_img=None, x_gender=None, y_age=None):
@@ -136,7 +136,7 @@ elif CNN == "Xception":
 # Gender input layer
 gdr_input = Input(shape=(1,), name="gdr_input")
 # Gender dense layer
-gdr_dense = Dense(32, activation="relu")
+gdr_dense = Dense(2, activation="relu")
 # Gender dense output
 output_gdr_dense = gdr_dense(gdr_input)
 
@@ -144,15 +144,19 @@ output_gdr_dense = gdr_dense(gdr_input)
 x = keras.layers.concatenate([output_cnn, output_gdr_dense])
 
 # We stack dense layers and dropout layers to avoid overfitting after that
+x = Dense(1256, activation="relu")(x)
+x = Dropout(0.35)(x)
 x = Dense(1000, activation="relu")(x)
-x = Dropout(0.45)(x)
-x = Dense(1000, activation="relu")(x)
-x = Dropout(0.45)(x)
-x = Dense(240, activation="relu")(x)
-# x = Dropout(0.1)(x)
+
+x1 = Dropout(0.35)(x)
+x1 = Dense(240, activation="relu")(x1)
+x2 = Dropout(0.35)(x)
+x2 = Dense(240, activation="relu")(x2)
+
+x = keras.layers.concatenate([x1, x2])
+# x = Dropout(0.2)(x)
 
 # and the final prediction layer as output (should be the main logistic regression layer)
-# predictions = Dense(1, activation='sigmoid', name='predictions')(x)
 predictions = Dense(1)(x)
 
 # Now that we have created a model structure we can define it
[…]

### 2018-09-11 trainingmonitor.py

@@ -7,13 +7,12 @@ import os
 
 
 class TrainingMonitor(BaseLogger):
-
-    def __init__(self, figPath, jsonPath=None, startAt=0):
+    def __init__(self, figPath, startAt=0):
         # store the output path for the figure, the path to the JSON
         # serialized file, and the starting epoch
         super(TrainingMonitor, self).__init__()
         self.figPath = figPath
-        self.jsonPath = jsonPath
+        self.jsonPath = os.path.sep.join([figPath, "female_and_male.json"])
         self.startAt = startAt
 
     def on_train_begin(self, logs={}):
@@ -29,7 +28,7 @@ class TrainingMonitor(BaseLogger):
                     # trim any entries that are past the starting
                     # epoch
                     for k in self.H.keys():
-                        self.H[k] = self.H[k][:self.startAt]
+                        self.H[k] = self.H[k][: self.startAt]
 
     def on_epoch_end(self, epoch, logs={}):
         # loop over the logs and update the loss, accuracy, etc.
@@ -49,16 +48,26 @@ class TrainingMonitor(BaseLogger):
         if len(self.H["loss"]) > 1:
             # plot the training loss and accuracy
             N = np.arange(0, len(self.H["loss"]))
+            # plot the training loss and accuracy
             plt.style.use("ggplot")
             plt.figure()
+
             plt.plot(N, self.H["loss"], label="train_loss")
             plt.plot(N, self.H["val_loss"], label="val_loss")
-            plt.plot(N, self.H["acc"], label="train_acc")
-            plt.plot(N, self.H["val_acc"], label="val_acc")
-            plt.title("Training Loss and Accuracy [Epoch {}]".format(len(self.H["loss"])))
+            plt.title("Training Loss [Epoch {}]".format(len(self.H["loss"])))
             plt.xlabel("Epoch #")
-            plt.ylabel("Loss/Accuracy")
-            plt.legend()
+            plt.ylabel("Loss")
+            plt.legend(loc="upper left")
             # save the figure
-            plt.savefig(self.figPath)
+            plt.savefig(os.path.sep.join([self.figPath, "history_loss.png"]))
+            plt.close()
+
+            plt.plot(N, self.H["mean_absolute_error"], label="train_mean")
+            plt.plot(N, self.H["val_mean_absolute_error"], label="val_mean")
+            plt.title("Training Absolute Error [Epoch {}]".format(len(self.H["loss"])))
+            plt.xlabel("Epoch #")
[…]

### 2018-09-12 check.py
New graph for show predicted and real values

@@ -31,7 +31,9 @@ PATH_SAVE_MODEL = os.path.join(__location__, "model_backup", GENDER_TYPE)
 def readFile(gender, dataset, X_img=None, x_gender=None, y_age=None):
     print("Reading", gender, dataset, "data...")
     file_name = gender + "-" + dataset + "-" + ".hdf5"
-    with h5py.File(os.path.join(__location__, "packaging-dataset", file_name), "r+") as f:
+    with h5py.File(
+        os.path.join(__location__, "packaging-dataset", file_name), "r+"
+    ) as f:
         f_img = f["img"][()]
         f_gender = f["gender"][()]
         f_age = f["age"][()]
@@ -120,11 +122,21 @@ for i in range(len(ynew)):
     print("ID:", i, "Original:", age_final[i], "Predict:", ynew[i][0])
 
 # summarize history for mean
-plt.plot(age_final, label="Real")
-plt.plot(ynew, label="Predict")
-plt.title("Age")
-plt.xlabel("Index")
-plt.ylabel("Age")
-plt.legend(["Real", "Predict"], loc="upper left")
+# plt.plot(age_final, label="Real")
+# plt.plot(ynew, label="Predict")
+# plt.title("Age")
+# plt.xlabel("Index of image")
+# plt.ylabel("Age")
+# plt.legend(["Real", "Predict"], loc="upper left")
+# plt.savefig(os.path.join(PATH_SAVE_MODEL, "predict_age.png"))
+# plt.show()
+
+_, ax1 = plt.subplots(1, 1, figsize=(6, 6))
+ax1.plot(ynew, "ro", label="predictions")
+ax1.plot(age_final, "b.", label="actual")
+ax1.set_title("Age")
+ax1.set_xlabel("Index of image")
+ax1.set_ylabel("Age")
+ax1.legend(["Real", "Predict"], loc="upper left")
 plt.savefig(os.path.join(PATH_SAVE_MODEL, "predict_age.png"))
 plt.show()

### 2018-09-12 check.py
Add style for mathplot

@@ -131,8 +131,9 @@ for i in range(len(ynew)):
 # plt.savefig(os.path.join(PATH_SAVE_MODEL, "predict_age.png"))
 # plt.show()
 
-_, ax1 = plt.subplots(1, 1, figsize=(6, 6))
-ax1.plot(ynew, "ro", label="predictions")
+plt.style.use("ggplot")
+_, ax1 = plt.subplots(1, 1, figsize=(24, 24))
+ax1.plot(ynew, "r.", label="predictions")
 ax1.plot(age_final, "b.", label="actual")
 ax1.set_title("Age")
 ax1.set_xlabel("Index of image")

### 2018-09-12 check.py
Accommodate predicted age graphs

@@ -22,7 +22,10 @@ GENDER_TYPE = "female_and_male"
 # GENDER_TYPE = "female"
 # GENDER_TYPE = "male"
 
+# Run evaluate method with only test data
 ONLY_TEST_IMAGE = True
+
+SHOW_PREDICT_TEST_DATA = False
 
 # Path to save model
 PATH_SAVE_MODEL = os.path.join(__location__, "model_backup", GENDER_TYPE)
@@ -118,26 +121,29 @@ print("Predict")
 # make a prediction
 ynew = model.predict(input_values)
 
-for i in range(len(ynew)):
-    print("ID:", i, "Original:", age_final[i], "Predict:", ynew[i][0])
-
-# summarize history for mean
-# plt.plot(age_final, label="Real")
-# plt.plot(ynew, label="Predict")
-# plt.title("Age")
-# plt.xlabel("Index of image")
-# plt.ylabel("Age")
-# plt.legend(["Real", "Predict"], loc="upper left")
-# plt.savefig(os.path.join(PATH_SAVE_MODEL, "predict_age.png"))
-# plt.show()
+if SHOW_PREDICT_TEST_DATA:
+    for i in range(len(ynew)):
+        print("ID:", i, "Original:", age_final[i], "Predict:", ynew[i][0])
 
 plt.style.use("ggplot")
+
+# summarize history for mean
 _, ax1 = plt.subplots(1, 1, figsize=(24, 24))
-ax1.plot(ynew, "r.", label="predictions")
-ax1.plot(age_final, "b.", label="actual")
-ax1.set_title("Age")
-ax1.set_xlabel("Index of image")
-ax1.set_ylabel("Age")
+ax1.plot(age_final, ynew, "r.", label="predictions")
+ax1.plot(age_final, age_final, "b-", label="actual")
+ax1.set_title("Boone age for test data")
+ax1.set_xlabel("Actual Age (Months)")
+ax1.set_ylabel("Predicted Age (Months)")
 ax1.legend(["Real", "Predict"], loc="upper left")
-plt.savefig(os.path.join(PATH_SAVE_MODEL, "predict_age.png"))
+plt.savefig(os.path.join(PATH_SAVE_MODEL, "predicted_age_for_test_data_graph_1.png"))
+plt.show()
+
+_, ax2 = plt.subplots(1, 1, figsize=(24, 24))
+ax2.plot(ynew, "r.", label="predictions")
[…]

### 2018-09-12 check.py
Add graph for check data

@@ -112,25 +112,27 @@ except:
 
 # evaluate loaded model on test data
 model.compile(optimizer=OPTIMIZER, loss="mean_squared_error", metrics=["MAE"])
+print("Evaluate model...")
 score = model.evaluate(input_values, age_final, batch_size=BATCH_SIZE, verbose=1)
 
 print("\nTest loss:", score[0])
 print("Test MAE:", score[1])
 
-print("Predict")
 # make a prediction
 ynew = model.predict(input_values)
 
 if SHOW_PREDICT_TEST_DATA:
+    print("Predict for test data")
     for i in range(len(ynew)):
         print("ID:", i, "Original:", age_final[i], "Predict:", ynew[i][0])
 
+# https://matplotlib.org/api/_as_gen/matplotlib.pyplot.plot.html#matplotlib.pyplot.plot
 plt.style.use("ggplot")
 
 # summarize history for mean
 _, ax1 = plt.subplots(1, 1, figsize=(24, 24))
 ax1.plot(age_final, ynew, "r.", label="predictions")
-ax1.plot(age_final, age_final, "b-", label="actual")
+ax1.plot(age_final, age_final, "b.", label="actual")
 ax1.set_title("Boone age for test data")
 ax1.set_xlabel("Actual Age (Months)")
 ax1.set_ylabel("Predicted Age (Months)")
@@ -146,4 +148,12 @@ ax2.set_xlabel("Actual Age (Months)")
 ax2.set_ylabel("Predicted Age (Months)")
 ax2.legend(["Real", "Predict"], loc="upper left")
 plt.savefig(os.path.join(PATH_SAVE_MODEL, "predicted_age_for_test_data_graph_2.png"))
-plt.show()
+
+_, ax3 = plt.subplots(1, 1, figsize=(24, 24))
+ax3.plot(age_final, ynew, "r.", label="predictions")
+ax3.plot(age_final, age_final, "b-", label="actual")
+ax3.set_title("Boone age for test data")
+ax3.set_xlabel("Actual Age (Months)")
+ax3.set_ylabel("Predicted Age (Months)")
+ax3.legend(["Real", "Predict"], loc="upper left")
+plt.savefig(os.path.join(PATH_SAVE_MODEL, "predicted_age_for_test_data_graph_3.png"))

### 2018-09-12 main.py

@@ -24,7 +24,7 @@ __location__ = os.path.realpath(os.path.join(os.getcwd(), os.path.dirname(__file
 
 # network and training
 EPOCHS = 50
-BATCH_SIZE = 32
+BATCH_SIZE = 16
 VERBOSE = 1
 # https://keras.io/optimizers
 OPTIMIZER = Adam(lr=0.001, amsgrad=True)
@@ -150,8 +150,13 @@ x = Dense(1000, activation="relu")(x)
 
 x1 = Dropout(0.35)(x)
 x1 = Dense(240, activation="relu")(x1)
+x1 = Dropout(0.2)(x1)
+x1 = Dense(120, activation="relu")(x1)
+
 x2 = Dropout(0.35)(x)
 x2 = Dense(240, activation="relu")(x2)
+x2 = Dropout(0.2)(x2)
+x2 = Dense(120, activation="relu")(x2)
 
 x = keras.layers.concatenate([x1, x2])
 # x = Dropout(0.2)(x)
@@ -256,7 +261,6 @@ score = model.evaluate(
 
 print("\nTest loss:", score[0])
 print("Test MAE:", score[1])
-# print("Test accuracy:", score[2])
 
 # Save all data in history
 with open(os.path.join(PATH_SAVE_MODEL, "history.pkl"), "wb") as f:
@@ -268,7 +272,7 @@ print(history.history.keys())
 
 # plot the training loss and accuracy
 plt.style.use("ggplot")
-plt.figure()
+plt.figure(figsize=(24, 24))
 
 plt.plot(history.history["loss"], label="loss")
 plt.plot(history.history["val_loss"], label="val_loss")
@@ -279,15 +283,6 @@ plt.legend(["train", "test"], loc="upper left")
 plt.savefig(os.path.join(PATH_SAVE_MODEL, "history_loss.png"))
 plt.close()
 
-# plt.plot(history.history["acc"], label="acc")
-# plt.plot(history.history["val_acc"], label="val_acc")
-# plt.title("Training Accuracy")
-# plt.xlabel("Epoch")
-# plt.ylabel("Accuracy")
-# plt.legend(["train", "test"], loc="upper left")
-# plt.savefig(os.path.join(PATH_SAVE_MODEL, "history_accuracy.png"))
-# plt.close()
-
 plt.plot(history.history["mean_absolute_error"], label="mean")
 plt.plot(history.history["val_mean_absolute_error"], label="val_mean")
 plt.title("Training Absolute Error")
[…]

### 2018-09-12 check.py
Show graph for train data and valid data

@@ -31,6 +31,74 @@ SHOW_PREDICT_TEST_DATA = False
 PATH_SAVE_MODEL = os.path.join(__location__, "model_backup", GENDER_TYPE)
 
 
+def generate_graph(x_img, x_gdr, y_age, title):
+    # https://matplotlib.org/api/_as_gen/matplotlib.pyplot.plot.html#matplotlib.pyplot.plot
+    plt.style.use("ggplot")
+
+    # I think there is another way to do this
+    input_values = x_img
+    try:
+        if model.get_layer(name="gdr_input") is not None:
+            print("Model with gender")
+            input_values = [x_img, x_gdr]
+    except:
+        pass
+
+    # make a prediction
+    y_new = model.predict(input_values)
+
+    if SHOW_PREDICT_TEST_DATA:
+        print("Predict for test data")
+        for i in range(len(y_new)):
+            print("ID:", i, "Original:", y_age[i], "Predict:", y_new[i][0])
+
+    # summarize history for mean
+    _, ax1 = plt.subplots(1, 1, figsize=(24, 24))
+    ax1.plot(y_age, y_new, "r.", label="predictions")
+    ax1.plot(y_age, y_age, "b.", label="actual")
+    ax1.set_title(title)
+    ax1.set_xlabel("Actual Age (Months)")
+    ax1.set_ylabel("Predicted Age (Months)")
+    ax1.legend(["Real", "Predict"], loc="upper left")
+    plt.savefig(
+        os.path.join(
+            PATH_SAVE_MODEL,
+            "predicted_" + title.lower().replace(" ", "_") + "_graph_1.png",
+        )
+    )
+    plt.show()
+
+    _, ax1 = plt.subplots(1, 1, figsize=(24, 24))
+    ax1.plot(y_age, y_new, "r.", label="predictions")
+    ax1.plot(y_age, y_age, "b-", label="actual")
+    ax1.set_title(title)
+    ax1.set_xlabel("Actual Age (Months)")
+    ax1.set_ylabel("Predicted Age (Months)")
+    ax1.legend(["Real", "Predict"], loc="upper left")
+    plt.savefig(
+        os.path.join(
+            PATH_SAVE_MODEL,
+            "predicted_" + title.lower().replace(" ", "_") + "_graph_1b.png",
+        )
+    )
+    plt.close()
+
+    _, ax1 = plt.subplots(1, 1, figsize=(24, 24))
[…]

### 2018-09-12 main.py
Fix plot label

@@ -24,7 +24,7 @@ __location__ = os.path.realpath(os.path.join(os.getcwd(), os.path.dirname(__file
 
 # network and training
 EPOCHS = 50
-BATCH_SIZE = 16
+BATCH_SIZE = 32
 VERBOSE = 1
 # https://keras.io/optimizers
 OPTIMIZER = Adam(lr=0.001, amsgrad=True)
@@ -150,13 +150,9 @@ x = Dense(1000, activation="relu")(x)
 
 x1 = Dropout(0.35)(x)
 x1 = Dense(240, activation="relu")(x1)
-x1 = Dropout(0.2)(x1)
-x1 = Dense(120, activation="relu")(x1)
 
 x2 = Dropout(0.35)(x)
 x2 = Dense(240, activation="relu")(x2)
-x2 = Dropout(0.2)(x2)
-x2 = Dense(120, activation="relu")(x2)
 
 x = keras.layers.concatenate([x1, x2])
 # x = Dropout(0.2)(x)
@@ -279,7 +275,7 @@ plt.plot(history.history["val_loss"], label="val_loss")
 plt.title("Training Loss")
 plt.xlabel("Epoch")
 plt.ylabel("Loss")
-plt.legend(["train", "test"], loc="upper left")
+plt.legend(["train", "test"], loc="upper right")
 plt.savefig(os.path.join(PATH_SAVE_MODEL, "history_loss.png"))
 plt.close()
 
@@ -288,7 +284,7 @@ plt.plot(history.history["val_mean_absolute_error"], label="val_mean")
 plt.title("Training Absolute Error")
 plt.xlabel("Epoch")
 plt.ylabel("Absolute Error")
-plt.legend(["train", "test"], loc="upper left")
+plt.legend(["train", "test"], loc="upper right")
 plt.savefig(os.path.join(PATH_SAVE_MODEL, "history_mean.png"))
 plt.close()
 
@@ -298,7 +294,7 @@ plt.plot(history.history["val_loss"], label="val_loss")
 plt.title("model loss")
 plt.ylabel("Loss")
 plt.xlabel("Epoch")
-plt.legend(["train", "test"], loc="upper left")
+plt.legend(["train", "test"], loc="upper right")
 plt.show()
 
 # summarize history for mean
@@ -307,7 +303,7 @@ plt.plot(history.history["val_mean_absolute_error"], label="val_mean")
 plt.title("Training Absolute Error")
 plt.xlabel("Epoch")
[…]

### 2018-09-12 check.py
Improve code on check file

@@ -22,10 +22,8 @@ GENDER_TYPE = "female_and_male"
 # GENDER_TYPE = "female"
 # GENDER_TYPE = "male"
 
-# Run evaluate method with only test data
-ONLY_TEST_IMAGE = True
-
-SHOW_PREDICT_TEST_DATA = False
+# Run evaluate model with all data set
+EVALUATE_WITH_ALL_DATA_SET = False
 
 # Path to save model
 PATH_SAVE_MODEL = os.path.join(__location__, "model_backup", GENDER_TYPE)
@@ -44,14 +42,22 @@ def generate_graph(x_img, x_gdr, y_age, title):
     except:
         pass
 
+    print("Evaluate model for", title.lower())
+    score = model.evaluate(input_values, y_age, batch_size=BATCH_SIZE, verbose=1)
+    print("Test loss:", score[0])
+    print("Test MAE:", score[1])
+
+    print("Predicted", title.lower())
+
     # make a prediction
     y_new = model.predict(input_values)
 
-    if SHOW_PREDICT_TEST_DATA:
+    if SHOW_PREDICT_DATA:
         print("Predict for test data")
         for i in range(len(y_new)):
             print("ID:", i, "Original:", y_age[i], "Predict:", y_new[i][0])
 
+    print("\nGenerate graphics...")
     # summarize history for mean
     _, ax1 = plt.subplots(1, 1, figsize=(24, 24))
     ax1.plot(y_age, y_new, "r.", label="predictions")
@@ -148,15 +154,11 @@ if GENDER_TYPE == "female_and_male" or GENDER_TYPE == "male":
     )
 
 print("Joining train, valid and test dataset.")
-if ONLY_TEST_IMAGE:
-    img_final = img_test
-    gdr_final = gdr_test
-    age_final = age_test
-else:
-    img_final = np.concatenate((img_train, img_valid, img_test), axis=0)
-    gdr_final = np.concatenate((gdr_train, gdr_valid, gdr_test), axis=0)
-    age_final = np.concatenate((age_train, age_valid, age_test), axis=0)
+img_final = np.concatenate((img_train, img_valid, img_test), axis=0)
+gdr_final = np.concatenate((gdr_train, gdr_valid, gdr_test), axis=0)
+age_final = np.concatenate((age_train, age_valid, age_test), axis=0)
 
+print("Loading model from disk")
 # load YAML and create model
[…]

### 2018-09-12 trainingmonitor.py

@@ -46,9 +46,8 @@ class TrainingMonitor(BaseLogger):
         # ensure at least two epochs have passed before plotting
         # (epoch starts at zero)
         if len(self.H["loss"]) > 1:
-            # plot the training loss and accuracy
             N = np.arange(0, len(self.H["loss"]))
-            # plot the training loss and accuracy
+            # plot the training loss
             plt.style.use("ggplot")
             plt.figure()
 

### 2018-09-12 main.py
Imptove model test mea 7.55

@@ -3,7 +3,7 @@
 
 from trainingmonitor import TrainingMonitor
 from keras.applications import InceptionV3, ResNet50, Xception
-from keras.layers import Flatten, Dense, Input, Dropout
+from keras.layers import Flatten, Dense, Input, Dropout, regularizers
 from keras.models import Model
 from keras.utils import plot_model
 from keras.optimizers import Adam, RMSprop, Adadelta, Adagrad
@@ -144,15 +144,25 @@ output_gdr_dense = gdr_dense(gdr_input)
 x = keras.layers.concatenate([output_cnn, output_gdr_dense])
 
 # We stack dense layers and dropout layers to avoid overfitting after that
-x = Dense(1256, activation="relu")(x)
+x = Dense(1000, activation="relu")(x)
 x = Dropout(0.35)(x)
 x = Dense(1000, activation="relu")(x)
 
 x1 = Dropout(0.35)(x)
-x1 = Dense(240, activation="relu")(x1)
+x1 = Dense(
+    240,
+    activation="relu",
+    kernel_regularizer=regularizers.l2(0.01),
+    activity_regularizer=regularizers.l1(0.01),
+)(x1)
 
 x2 = Dropout(0.35)(x)
-x2 = Dense(240, activation="relu")(x2)
+x2 = Dense(
+    240,
+    activation="relu",
+    kernel_regularizer=regularizers.l2(0.01),
+    activity_regularizer=regularizers.l1(0.01),
+)(x2)
 
 x = keras.layers.concatenate([x1, x2])
 # x = Dropout(0.2)(x)
@@ -268,7 +278,7 @@ print(history.history.keys())
 
 # plot the training loss and accuracy
 plt.style.use("ggplot")
-plt.figure(figsize=(24, 24))
+# plt.figure(figsize=(24, 24))
 
 plt.plot(history.history["loss"], label="loss")
 plt.plot(history.history["val_loss"], label="val_loss")

### 2018-09-12 prueba.py
Delete old file

@@ -1,28 +1,0 @@
-"""
-import tensorflow as tf
-hello = tf.constant('Hello, TensorFlow!')
-sess = tf.Session()
-print(sess.run(hello))
-
-    edges = cv2.Canny(img_rotation,50,150,apertureSize = 3)
-    minLineLength = 100
-    maxLineGap = 5
-    lines = cv2.HoughLinesP(edges,1,np.pi/180,15,minLineLength,maxLineGap)
-    for x in range(0, len(lines)):
-        for x1,y1,x2,y2 in lines[x]:
-            cv2.line(img_rotation,(x1,y1),(x2,y2),(0,255,0),2)
-
-    num_rows, num_cols = imageToRotate.shape[:2]
-    rotation_matrix = cv2.getRotationMatrix2D((num_cols/2, num_rows/2), 0, 1)
-    img_rotation = cv2.warpAffine(img, rotation_matrix, (num_cols, num_rows))
-"""
-import numpy as np
-age_train = np.array([1, 2, 3, 4, 5, 6])
-gdr_train = np.array([10, 20, 30, 40, 50, 60])
-
-random_no = np.random.choice(age_train.shape[0], size=age_train.shape[0], replace=False)
-
-print(gdr_train[0], age_train[0])
-age_train = age_train[random_no]
-gdr_train = gdr_train[random_no]
-print(gdr_train[0], age_train[0])

### 2018-09-13 autoencoder/index.py
Fist example autoencoder

@@ -1,0 +1,71 @@
+from keras.layers import Input, Dense, Conv2D, MaxPooling2D, UpSampling2D
+from keras.models import Model
+from keras import backend as K
+from keras.datasets import mnist
+import matplotlib.pyplot as plt
+import numpy as np
+
+(x_train, _), (x_test, _) = mnist.load_data()
+
+x_train = x_train.astype("float32") / 255.
+x_test = x_test.astype("float32") / 255.
+x_train = np.reshape(
+    x_train, (len(x_train), 28, 28, 1)
+)  # adapt this if using `channels_first` image data format
+x_test = np.reshape(
+    x_test, (len(x_test), 28, 28, 1)
+)  # adapt this if using `channels_first` image data format
+
+########################### Auto encoder ############################
+input_img = Input(
+    shape=(28, 28, 1)
+)  # adapt this if using `channels_first` image data format
+
+x = Conv2D(16, (3, 3), activation="relu", padding="same")(input_img)
+x = MaxPooling2D((2, 2), padding="same")(x)
+x = Conv2D(8, (3, 3), activation="relu", padding="same")(x)
+x = MaxPooling2D((2, 2), padding="same")(x)
+x = Conv2D(8, (3, 3), activation="relu", padding="same")(x)
+encoded = MaxPooling2D((2, 2), padding="same")(x)
+
+# at this point the representation is (4, 4, 8) i.e. 128-dimensional
+
+x = Conv2D(8, (3, 3), activation="relu", padding="same")(encoded)
+x = UpSampling2D((2, 2))(x)
+x = Conv2D(8, (3, 3), activation="relu", padding="same")(x)
+x = UpSampling2D((2, 2))(x)
+x = Conv2D(16, (3, 3), activation="relu")(x)
+x = UpSampling2D((2, 2))(x)
+decoded = Conv2D(1, (3, 3), activation="sigmoid", padding="same")(x)
+
+autoencoder = Model(input_img, decoded)
+autoencoder.compile(optimizer="adadelta", loss="binary_crossentropy")
+
+autoencoder.fit(
+    x_train,
+    x_train,
+    epochs=150,
+    batch_size=128,
+    shuffle=True,
+    validation_data=(x_test, x_test),
+)
+
+decoded_imgs = autoencoder.predict(x_test)
+
+n = 10
+plt.figure(figsize=(20, 4))
+for i in range(1, n + 1):
[…]

### 2018-09-13 autoencoder.py
Fix check script

@@ -1,0 +1,110 @@
+from keras.layers import Input, Dense, Conv2D, MaxPooling2D, UpSampling2D
+from keras.models import Model
+from keras import backend as K
+from keras.datasets import mnist
+import matplotlib.pyplot as plt
+import h5py
+import numpy as np
+import os
+
+__location__ = os.path.realpath(os.path.join(os.getcwd(), os.path.dirname(__file__)))
+
+
+def readFile(gender, dataset, X_img=None, x_gender=None, y_age=None):
+    print("Reading", gender, dataset, "data...")
+    file_name = gender + "-" + dataset + "-" + ".hdf5"
+    with h5py.File(
+        os.path.join(__location__, "packaging-dataset", "for_autoencoder", file_name),
+        "r+",
+    ) as f:
+        f_img = f["img"][()]
+        f_gender = f["gender"][()]
+        f_age = f["age"][()]
+        f.close()
+    if X_img is None:
+        X_img = f_img
+    else:
+        X_img = np.concatenate((X_img, f_img), axis=0)
+
+    if x_gender is None:
+        x_gender = f_gender
+    else:
+        x_gender = np.concatenate((x_gender, f_gender), axis=0)
+
+    if y_age is None:
+        y_age = f_age
+    else:
+        y_age = np.concatenate((y_age, f_age), axis=0)
+
+    return X_img, x_gender, y_age
+
+
+######################################################################
+(x_train, _), (x_test, _) = mnist.load_data()
+x_train = x_train.astype("float32") / 255.
+x_test = x_test.astype("float32") / 255.
+x_train = np.reshape(
+    x_train, (len(x_train), 28, 28, 1)
+)  # adapt this if using `channels_first` image data format
+x_test = np.reshape(
+    x_test, (len(x_test), 28, 28, 1)
+)  # adapt this if using `channels_first` image data format
+######################################################################33
+genderType = "male"
+genderType = "female"
+# x_test, _, _ = readFile(genderType, "testing")
+# x_train, _, _ = readFile(genderType, "validation")
+# input_img = Input(shape=x_train.shape[1:])
+
+input_img = Input(shape=(28, 28, 1))
+########################### Auto encoder ############################
[…]

### 2018-09-13 autoencoder/index.py

@@ -1,71 +1,0 @@
-from keras.layers import Input, Dense, Conv2D, MaxPooling2D, UpSampling2D
-from keras.models import Model
-from keras import backend as K
-from keras.datasets import mnist
-import matplotlib.pyplot as plt
-import numpy as np
-
-(x_train, _), (x_test, _) = mnist.load_data()
-
-x_train = x_train.astype("float32") / 255.
-x_test = x_test.astype("float32") / 255.
-x_train = np.reshape(
-    x_train, (len(x_train), 28, 28, 1)
-)  # adapt this if using `channels_first` image data format
-x_test = np.reshape(
-    x_test, (len(x_test), 28, 28, 1)
-)  # adapt this if using `channels_first` image data format
-
-########################### Auto encoder ############################
-input_img = Input(
-    shape=(28, 28, 1)
-)  # adapt this if using `channels_first` image data format
-
-x = Conv2D(16, (3, 3), activation="relu", padding="same")(input_img)
-x = MaxPooling2D((2, 2), padding="same")(x)
-x = Conv2D(8, (3, 3), activation="relu", padding="same")(x)
-x = MaxPooling2D((2, 2), padding="same")(x)
-x = Conv2D(8, (3, 3), activation="relu", padding="same")(x)
-encoded = MaxPooling2D((2, 2), padding="same")(x)
-
-# at this point the representation is (4, 4, 8) i.e. 128-dimensional
-
-x = Conv2D(8, (3, 3), activation="relu", padding="same")(encoded)
-x = UpSampling2D((2, 2))(x)
-x = Conv2D(8, (3, 3), activation="relu", padding="same")(x)
-x = UpSampling2D((2, 2))(x)
-x = Conv2D(16, (3, 3), activation="relu")(x)
-x = UpSampling2D((2, 2))(x)
-decoded = Conv2D(1, (3, 3), activation="sigmoid", padding="same")(x)
-
-autoencoder = Model(input_img, decoded)
-autoencoder.compile(optimizer="adadelta", loss="binary_crossentropy")
-
-autoencoder.fit(
-    x_train,
-    x_train,
-    epochs=150,
-    batch_size=128,
-    shuffle=True,
-    validation_data=(x_test, x_test),
-)
-
-decoded_imgs = autoencoder.predict(x_test)
-
-n = 10
-plt.figure(figsize=(20, 4))
-for i in range(1, n + 1):
[…]

### 2018-09-13 check.py

@@ -28,6 +28,9 @@ EVALUATE_WITH_ALL_DATA_SET = False
 # Path to save model
 PATH_SAVE_MODEL = os.path.join(__location__, "model_backup", GENDER_TYPE)
 
+# Show result on terminal
+SHOW_PREDICT_DATA = False
+
 
 def generate_graph(x_img, x_gdr, y_age, title):
     # https://matplotlib.org/api/_as_gen/matplotlib.pyplot.plot.html#matplotlib.pyplot.plot
@@ -164,11 +167,12 @@ yaml_file = open(os.path.join(PATH_SAVE_MODEL, "model.yaml"), "r")
 loaded_model_yaml = yaml_file.read()
 yaml_file.close()
 model = model_from_yaml(loaded_model_yaml)
-# load weights into new model
-model.load_weights(os.path.join(PATH_SAVE_MODEL, "model.h5"))
 
 # printing a model summary to check what we constructed
 print(model.summary())
+
+# load weights into new model
+model.load_weights(os.path.join(PATH_SAVE_MODEL, "model.h5"))
 
 # evaluate loaded model on test data
 model.compile(optimizer=OPTIMIZER, loss="mean_squared_error", metrics=["MAE"])
